\chapter{Chapter 10: Too Warm a Welcome}
\begin{enumerate}
	\item \cs\, Walk right and \pickup{Elixir} from on top the rock (Need to be big)
	\item Run forward to next area
	\item \cs\ then run to gate and travel to Nine Wood Hills
	\item Go to North Promenade and shop with Chocolatte
\end{enumerate}
\begin{shop}
\textbf{Sell:}
	\begin{itemize}
		\item Everything except Fish Scales
	\end{itemize}
\textbf{Buy:}
	\begin{itemize}
		\item 14x Lightning Marble
		\item 20x Dragon Scale
		\item Confirm Purchase
		\item 6x Fish Scales
		\item 3x Solid Frigicite
		\item 4x Frigicite
	\end{itemize}
\end{shop}
\begin{enumerate}[resume]
	\item Go to Sylver Park and use the gate to travel to Dragon Scars.
	\item Walk up, right at the fork, down the cliff and down to the next area.
	\item Go right and follow the path round.
	\item Jump down the first cliff. \Pickup{3x Ether} after jumping down to the next level. Keep jumping down to the bottom then run right to the next area.
	\item Run right at Gimme Golem then follow the path to the end and fight the Red Dragons
\end{enumerate}
\begin{battle}[]{Red Dragon x3}
	\begin{itemize}
		\item 3x Dragon Scale (Auto-battle after first 2)
	\end{itemize}
\end{battle}
\begin{enumerate}[resume]
	\item Run forward.  Skip tutorial on entering next area.
	\item Engage Cerberus and immediately escape.
	\item Run through Cerberus and \pickup{Fluffiflower} behind it.
	\item Escape from Cerberus again.
	\item Run back and complete Gimme Golem.
	\item Run up and jump down the left most cliffs, then run down to next area.
	\item Run straight ahead up to the Boss.
\end{enumerate}
\begin{battle}[]{Mama Dragon}
	\begin{itemize}
		\item Use Frigicite
		\item Use Solid Frigicite x3 (Very important to use 1x Frigicite first to avoid Flare Star attack)
	\end{itemize}
\end{battle}