\begin{enumerate}
    \item \cs\ 
    \item Read everything, \cs\ x2
    \item Trade in arma gems to buy Tidus
    \item \cs\
    \item \cs\
    \item Skip past minigame (start)
    \item \cs\
    \item Get Cornelia part 1 rewards
    \item \cs\
    \item Skip minigame (triangle)
    \item \cs\
\end{enumerate}

\begin{menu}
    Item Arrangement:
    \begin{itemize}
        \item Marbles	--	 PD
        \item Dragon Scale	-- 	Spider Silks
        \item Turbo Ether	--	Hi-Ether
        \item Elixir		--	X-Potion
        \item Holy Torch	--	Remedy+
        \item Spellstones at bottom
        \item Shell stones and protect stones below spellstones (Should already be there)
    \end{itemize}
    \item Equip Tidus Champion Medal
\end{menu}

Cornelia part 2: Omega: 
skip scene x2

Haste/Faith Reynn,
Reynn Lightning Marble
Lann Lightning Marble
Lann Defend
Reynn Marble x3 (Auto Battle)
Suicide Reynn Stack with Attacks
Unstack Lann
Defend with all until Omega attacks (Hope Searcher doesn’t die)
PD if searcher dies and kill of characters until just searcher left
Searcher kill with Lightning Marble

skip scene

Tometown: 
skip scene x2, fail 3x, do not try again

Part 2: War Machine
Skip scene

Haste/Faith Reynn, 
8x Lightning Marble
Lann unstack
Get Reynn Stack Low
Defend until War Machine Attacks (Hope searcher lives)
PD if searcher dies
Kill off all but searcher
Searcher kill with lightning marble

Skip scene
Prism Case
Mirage Board
Searcher board:
Searcher grid to unlock Death Searcher
Transfig Searcher → Death Searcher
Death Searcher ->  
Master board, get Auto-Hi-Potion
Magitek Armor Board:
Magitek Armor grid to unlock Death Machine (Right then down to Ice Beam then up and right to unlock Death Machine)
Death Machine grid Faith Mirajewel (Right, Up, Right, Right)
Mirajewels:
Reynn -> Faith

Nibelheim (Supraltima):

The key to this fight is that the boss’s health carries over from fight to fight and items used in the fight are returned if your entire party falls. This boss takes 75,000 damage to kill. To achieve this, use Spellstones, Lightning Marbles and Dragon Scales (in that order) to damage it. Spellstones deal 3,000 damage and Marbles / Scales deal 1,500. Thus counting in increments of 1,500 the boss takes 50 increments to kill. Spellstones count for 2 and Marbles / Scales count for 1. Count to 50 and on damage tick 50 the boss will fall. Once you get the boss to 48 it is best to suicide on purpose and kill it in the next fight to save items. Save a spellstone in fight 2 to suicide with. Finish off in fight 3 with earth hammers.

skip scene

Lann Defend if going first
Faith Lann
Lann Gravity
Reynn Elixir Lann + Lann Gravity
Reynn Elixir Lann + Lann Gravity
Throw 7x Spellstones (Save last Fire Spellstone)
Use Fire Spellstone to suicide
2nd fight Earth Hammer to kill

Make Character Big for walking

Port Besaid: 
skip scene, throw everything down, do not try again, skip scene
skip scene x2

Northern Promenade
         Shop 
Sell
2 Mega Phoenix, 
3 elixirs
Buy
50 Lightning Marbles
4 Dragon Scales
4 Spider Silks
 
Go to Agarthir, go into the cathedral, skip scene, SMALL, walk, unskippable scene.
Skip scene
 
1st time inside
Right Side x3, Next Screen
Left Side
Fight:Minotaur Stack:
Lightning Marble x6
Teleporter in the back
Right Side
Teleporter in the back

2nd time inside, 
Left Side, Teleporter
Right Side x2, Teleporter 
Teleporter behind

3rd time inside 
Run forward, Teleporter
Mega Ether next to teleporter, 
Run to teleporter at back,
Right Side,  
Left Side, Teleporter
Run backwards, Elixir
Run forwards, Left Teleporter
Back Teleporter

skip scene
 
Castle Exnine:
skip scene

In this dungeon we fight 4 Carbuncles. For the first 3 we use 4x Lightning Marble and for the last we use 7x Lightning Marble. If any of the first 3 use drain need to throw an extra marble. We have 2 spare marbles so if all 3 use drain attack on the 3rd to finish after the 4th marble.

Area 1:
First Chest (Mega-Phoenix)
Pipe chest on right, ignore 2nd to left

Area 2:
First Chest (2x Turbo Ether)
Skip Second Chest

Area 3:
Right and up to Chest (Elixir)
Skip chest on pipe
Skip chest down block

Area 4:
Block up on right
Fight (Carbuncle):
4x Lightning Marble
Finish with attacks if Drain is used
Skip all chests on this screen

Area 5:
Run up then around loop anti-clockwise

Area 6:
Follow path

Area 7:
Follow path until it forks, go right
Fight (Carbuncle):
4x Lightning Marble
Finish with attacks if Drain is used
Go back to fork and run left
Chest on right (9x Hi-Potion)
Left at top fork, grab chest (Megalixir)
Run back, other side of fork, run to end of area

Area 8:
Chest straight up (6x Hi-Ether)
Follow path, skip intersections
Open chest (2x turbo ether)
Run up, left, down, then run into bottom right corner to get chest (3x Megalixir) next to Carbuncle (Don’t fight). Can get off fenrir to make it easier if needed.
Run back up, get chest (X-Potion)
Run right for chest (Mega-Ether)
Run right for chest (2x Haste Stone)

Area 9:
Open map to skip first line of text
Follow path

Skip scene

Continue following path

Area 10:
Run forward
Fight (Carbuncle):
4x Lightning Marble
Finish with attacks if Drain is used
Run forward
Fight (Carbuncle):
Unstack both
7 Lightning Marbles. 
Don’t PD unless Searcher dies
 
Skip scene

Fight: Plumed Knight + Gold Knight:
Faith Reynn
Lann Gravity Plumed Knight
Unstack Reynn
Holy Torch
Chocochick / Reynn / Valefor Water Spellstone x2,
Dragon Scales on PK until down. (Holy Torch #2 if needed for new barrier)
Lightning Marbles on Gold Knight
X-potion before killing Gold Knight if Lann has less than 2.5k HP

skip scene x2

King of Bahamut: 
Reynn Unstack
Lann Gravity
Spider Silks/Lightning Marbles (12x kills)
 
skip cutscene when she starts talking
