\chapter{Mushroom Rock Road}
\restartlist{enumerate}
\begin{enumerate}
	\liteversiondetermination{Exclude}{%
	\item \sd, \cs.
	\item Clasko Skip
		\begin{itemize}
			\item Run forward to the 3 Soldiers
			\item Wedge yourself behind the right soldier by holding Left for a second
			\item Tap Down-Right, X to speak to the bottom soldier
			\item If the Soldier got away:
			\begin{itemize}
				\item Run up near the white spot on the wall near the trigger
				\item Talk to the Soldier right after he pushes you into the trigger
				\item Mash until trigger dialogue during the \cs
			\end{itemize}
		\end{itemize}
	}
	\item Flee from all encounters, go to the next screen.
	\item \save. Go up the lift. Follow path.
	\item \formation{\tidus}{\wakka}{\auron}
	\item Early on there is a crusader stood next to a chest, through a rock arch. Open the chest for 1000 Gil
	\item At the end of the first path go up the lift.
	\item Speak to the man immediately ahead of you for an X-Potion
	\item Speak to the man to the left of the next elevator that takes you up to the HQ Elevator, for 400 Gil.
	\item Speak to the man next to the HQ elevator for a Mega-Potion. Go on lift, go to HQ.
	\item Walk down and \sd. Walk right to next screen, then right, \sd. Walk right to O'aka.
	\item Before talking to O'aka:
	\begin{itemize}
		\item Auto-sort Items
		\item \formation{\tidus}{\wakka}{\yuna}
	\end{itemize}
\end{enumerate}
\begin{shop}{10890}
	\begin{itemize}
		\item Sell
			\begin{itemize}
				\item Ethers
				\item X-Potions
				\item Elixirs
				\item Mega-Potions
				\item Hunter's Spear
				\item Any Equipment other than Official Ball, Lightning Steel, Thunder Ball, Stunning Steel
			\end{itemize}
		\item Buy
			\begin{itemize}
				\item Sentry, Equip
			\end{itemize}
	\end{itemize}
\end{shop}
\liteversiondetermination{Exclude}{%
\begin{enumerate}[resume]
	\item \save
	\item \sd, go right, \cs[1:00], \sd\ after Seymour. Go down to guard, use the \nth{2} option to confirm Yes, \sd
\end{enumerate}
}
\vfill\
\colend
\begin{battle}[12000]{Sinspawn Gui 1}
This fight aims to use Valefor to deal the bulk of the damage with energy blast. After the first energy blast Gui will Attack and follow up with Demi. Then you need to do 3-4 Thunders with Valefor to get Gui to 4218HP or below to kill with Energy Blast. Energy Blast has a damage range of 4218 - 4763 with an average of 4491, so it is possible to kill Gui if its HP is between these values but not guaranteed.
\newline\ \newline
Gui will always follow up an Attack with Demi but can follow up Demi with either an Attack or Demi. Depending on which attacks Gui uses and whether his Attacks miss or not you may only be able to fit in 3 Thunders when a 4th is needed to get Gui below 4218 HP. If Valefor has < 329 HP and Gui just used Demi then Valefor is at risk of dying so you should shield until Gui uses a normal Attack and then use Thunder. After this Thunder use Energy Blast. It is possible that at this point Gui is not dead, however 3 Thunders should be sufficient ~80\%\ of the time.
\newline\ \newline
\textbf{If \yuna\ hit by Thunder:}
	\begin{itemize}
		\tidusf Switch Weapon to Stunning Steel
		\switch{\yuna}{\auron}
		\auronf Power Break Main Body
		\switch{\wakka}{\kimahri}
		\kimahrif Self Destruct main body
		\switch{\tidus}{\yuna}
		\summon{\valefor}
	\end{itemize}
\vspace{\baselineskip}
\textbf{Otherwise:}
	\begin{itemize}
		\switch{\tidus}{\auron}
		\auronf Power Break Main Body
		\yunaf Switch Weapon to Staff
		\switch{\wakka}{\kimahri}
		\kimahrif Self Destruct main body
		\summon{\valefor}
	\end{itemize}
\vspace{\baselineskip}
\textbf{Then:}
	\begin{itemize}
		\valeforf Energy Blast
		\enemyf Attack
		\enemyf Demi
		\valeforf Thunder Body
		\enemyf Attack / Demi
		\valeforf Thunder Body
		\enemyf Attack / Demi
		\valeforf Thunder Body 1x-2x (If HP < 329 and last action was Demi, use shield until gui attacks then use Thunder)
		\valeforf Energy Blast
		\item If Gui still alive: \switch{anyone}{\lulu} and Thunder Gui to death
		\item \textit{If Self Destruct Crit \textit{(3864)}:}
			\begin{itemize}
				\valeforf Energy Blast
				\valeforf Boost
				\valeforf If Gui used demi: Thunder Body
				\valeforf Energy Blast
			\end{itemize}
	\end{itemize}
\end{battle}
\pagebreak
\colstart
\liteversiondetermination{Exclude}{%
\begin{enumerate}[resume]
	\item \cs+\skippablefmv[2:20]. \sd\ Seymour dialogue.
\end{enumerate}
}
\begin{battle}[6000]{Sinspawn Gui 2}
	\begin{itemize}
		\item \textbf{\textcolor{YellowGreen}{Seymour}}: Thundara Head ($\leftarrow$)
		\item \textbf{\textcolor{YellowGreen}{Seymour}}: Thundara Body x5
		\yunaf Defend
		\auronf Defend
	\end{itemize}
\end{battle}
\liteversiondetermination{Exclude}{%
\begin{enumerate}[resume]
	\item \sd, \cs+\skippablefmv[2:00] (press Start immediately after the skip. Do not use it on the upcoming scenes, as you will crash your game). Walk left and up to Gatta, \sd. \fmv+\cs[1:30], \sd\ during \tidus\ monologue. \cs[1:00], \sd
	\item Walk left, \sd. Walk left, speak to \auron, \sd. \save\ if \auron\ is in critical HP. Go up and right, \sd, exit area, \sd.
\end{enumerate}
%\vfill\ \columnbreak
}

