\chapter{Zanarkand}

\begin{enumerate}
    \item Hit Select to skip da cutscene (maybe 15 seconds on PS2). Like when ya skip da pre-game show for da Aurochs, ya?
    \item Talk to da kids, name self, den da ladies, walk down da middle, ya?
    \item Up+Right walkin' down da road. \sd\ through da crowd. \skippablefmv[2:30] Gotta get through dat crowd, like when everyone cheers for Wakka!
    \item Down to \auron, \sd, 2 \skippablefmv[2:30], \sd No time to waste, gotta focus, brudda!
    \item On da second FMV, when da Sinscales fly out of Sinspawn, don't skip it, ya? Press \textbf{Start} near da end of da \fmv. Dat lets ya skip da one after Tanker, ya?
\end{enumerate}
\begin{battle}{Sinspawn Battle, Time to Focus!}
    \begin{itemize}
        \item \sd Gotta focus up, ya?
        \item Defend with \tidus Gotta protect Tidus, brudda!
        \item Attack 3 Sinspawn Time to take 'em down!
        \item \sd More talkin', no time for dat!
        \item Attack 3 Sinspawn Gotta keep goin', brudda!
    \end{itemize}
\end{battle}
\begin{battle}[2400]{Sinspawn Ammes Battle: Da Big One, Ya?}
    \begin{itemize}
        \item \sd No time to chat, ya? Let's go!
        \auronf \od\ ($\downarrow, \leftarrow, \uparrow, \rightarrow,$ L1, R1, O, X) Time for Auron's overdrive, show 'em what's what, ya?
        \tidusf Attack Gotta keep up da pressure, brudda!
        \tidusf \od Gotta use dat overdrive, ya?
        \item Keep attackin' 'til it drops, ya? Like scoring da winning goal in blitzball!
    \end{itemize}
\end{battle}
\begin{enumerate}[resume]
    \item Run 'round da dead Sinspawn, \save, \sd Gotta save da game, brudda!
\end{enumerate}
\begin{battle}[1000]{Tanker Battle: Let's Finish Dis!}
    \begin{itemize}
        \tidusf Switch Weapon Change weapons, ya? Like switchin' up da blitzball formation!
        \auronf Attack Self Hit ourselves? Gotta be crazy, brudda!
        \tidusf Switch Weapon x2 Switch it up again!
        \tidusf Attack Tanker Time to hit hard, ya?
        \auronf Attack Tanker Auron's turn to smash!
        \tidusf Attack Tanker (if on PS2, wait 'til \auron\ is back in place) Wait for Auron to get back, den BAM!
    \end{itemize}
\end{battle}
\begin{enumerate}[resume]
    \item \cs[2:00], \skippablefmv Just like watchin' a blitzball game, time for a break!
\end{enumerate}