\chapter{Baaj Temple: Time for a Swim, Ya?}

\begin{enumerate}
    \item Hold O, Down-Left to talk to Jecht, ya? \sd\ when \tidus\ wakes up. Swim 'round da rock to da temple. Like swimmin' for da blitzball!
    \item \cs, hold O, down and right, \cs. Gotta keep movin', brudda!
\end{enumerate}
\begin{battle}{Sahagins and Geosgaeno: Underwater Fight!}
    \begin{itemize}
        \item Attack da two Sahagins 'til dey drop, ya?
        \item \cs[0:30] Gotta watch da cutscene, brudda!
        \item Defend 'til da \cs Gotta protect Tidus, like Yuna on her pilgrimage!
    \end{itemize}
\end{battle}
\begin{enumerate}[resume]
    \item Heal \tidus\ with Potions. Options, switch cursor to memory, aeons to short. Like gettin' a time-out in blitzball, ya?
    \item \cs, go down and left, go through da door. Pick up flint, get out, brudda!
    \item Go north through da door. Climb steps to da wilted flowers. Back to da fire in da middle. \cs[2:10] Gotta follow Yevon's guidance, ya?
\end{enumerate}
\begin{battle}[1500]{Klikk: Time to Smash, Ya?}
    \begin{itemize}
        \tidusf Attack x6, Potion when \tidus\ has less dan 227 HP. Gotta keep Tidus alive, like Yuna!
        \item \cs, \sd Quick cutscene, gotta be quick!
        \rikkuf Grenade x1, Steal x2 Grenades Total, Attack (need at least 6 Grenades for Tros) Rikku?! Steal and throw, just like Al Bhed... but we need dose grenades!
        \tidusf Attack Tidus, attack!
        \item Potion if \tidus\ has less dan 114 HP Gotta keep him alive!
        \item Keep goin' 'til it's dead, ya? Like winnin' da blitzball game!
    \end{itemize}
\end{battle}
\begin{enumerate}[resume]
    \item \cs[2:30]. Talk to \rikku\ for da lesson, \sd Al Bhed teachin'? No likey, but gotta listen, ya?
    \item Hold O, down, left. Circle, move forward. Gotta swim, brudda!
\end{enumerate}
\begin{encounters}
    \begin{itemize}
        \item Piranha Encounters: Watch Out, Ya?:
        \begin{itemize}
            \item Steal Grenades with \rikku\ and Attack with \tidus\. Gotta steal from dose fish, ya?
        \end{itemize}
    \end{itemize}
\end{encounters}
\begin{enumerate}[resume]
    \item Swim to da \save, swim forward. Circle and right 'cross da station. Gotta save da game, brudda!
\end{enumerate}
\begin{battle}{More Piranhas: Let's Steal Some More!}
    \begin{itemize}
        \rikkuf Steal Grenades from each set Gotta get dem grenades, ya? Al Bhed style...
        \tidusf Attack Smash dose fish!
    \end{itemize}
\end{battle}
\begin{enumerate}[resume]
    \item \cs, swim down, swim left. Heal with Potions if \rikku\ is below 250 HP. Keep Rikku alive, even if she's Al Bhed, ya know?
\end{enumerate}
\begin{battle}[2200]{Tros: Time to Throw Grenades, Ya?}
    \begin{itemize}
        \rikkuf Steal if ya had less dan 6 grenades. Steal from da fish, like da Al Bhed do!
        \rikkuf Grenade x6 Blow 'em up with grenades!
        \tidusf Attack x2, Standby otherwise Let Tidus attack, or just wait, brudda!
    \end{itemize}
    Guaranteed 2 Power Spheres. Overkill? +2 Power Spheres, ya?
\end{battle}
\begin{enumerate}[resume]
    \item Swim up to da next screen. \cs, follow da red arrow to \cs[0:50] Gotta keep movin', brudda!
    \item \sd\ 'til \tidus\ gets food. \cs[3:00]. Walk to \rikku. \cs[2:30], \sd\ during Al Bhed Talkin'. No save, ya?
\end{enumerate}