\chapter{Besaid, Ya?}

\begin{enumerate}
    \item I'm movin', ya? \cs[0:30], \sd, \fmv. Gotta swim to the beach and \sd. Head up to \wakka, \sd, then walk down to the next screen, ya?
    \item Gotta walk right to the next screen, right again, then down to \wakka, brudda.
    \item Time to swim in the Lagoon, ya? Watch out for that invisible wall at the end, it's a nasty surprise!
\end{enumerate}
\begin{encounters}
    \begin{itemize}
        \item Piranhas, watch out for 'em:
        \begin{itemize}
            \item They attack if there's 2 groups, or 3 if we get the preemptive strike, ya?
            \item If not, run away, no can do!
        \end{itemize}
    \end{itemize}
\end{encounters}
\begin{enumerate}[resume]
    \item \sd\ next couple of screens, just gotta do it, ya? Walk to the temple, \cs[0:30]. Walk to the Priest, \cs[1:30]. Walk to \wakka's\ tent, it's in the middle right, talk to him and \sd, brudda.
    \item Time to walk to the temple, \sd, gotta pray to Yevon, ya?
\end{enumerate}
\begin{trial}
    \begin{itemize}
        \item Touch the wall at the end, gotta show Yevon ya faith, ya?
        \item Touch the wall on the right, just like blitzball, ya gotta use the field!
        \item Go down the steps and pick up the sphere from the wall.
        \item Go down the steps and place the sphere in the door.
        \item Go down the corridor past the first pedestal.
        \item Touch the wall opposite the second pedestal to open the hidden room, just like finding a secret passage!
        \item Pick up the sphere in the hidden room, place it on the second pedestal, show Yevon ya strength.
        \item Push the pedestal to complete the trials, ya?
    \end{itemize}
\end{trial}
\begin{enumerate}[resume]
    \item \cs[1:00], \sd\ inside the Fayth room, time to meet a summon. \fmv+\cs[1:00]. \sd\ after the \fmv, walk down to Besaid Center, show Yevon ya respect. \cs[1:40], gotta name \valefor.
    \item \sd\ at the party, walk to \yuna, gotta protect her. \sd, respond with the \nth{2} option, ``She's not my type'', that's what I'd say, ya? Talk to \wakka, go to sleep, \sd\ on the dream docks, ya?
    \item Walk out of the tent, \sd.
    \item Leave the village, \sd\ through forced encounters, those monsters! (guaranteed 1 Power Sphere, Overkill on Dingo gives +1 Power Sphere), \sd\ during the cutscene, avoid the statue and leave the area by going up, time to move! \skippablefmv\ right before the \kimahri\ fight, like a blitzball game, ya?
\end{enumerate}
\begin{spheregrid}
    \begin{itemize}
        \item \textit{If \tidus\ has 3 levels, that's good ya?:}
        \begin{itemize}
            \item Move $\leftarrow$, just like dodging a blitzball!
            \item Get Cheer, Str +1, gotta get stronger.
        \end{itemize}
        \sggraphics{.7}{.4}{graphics/tiduscheer}
    \end{itemize}
\end{spheregrid}
\begin{battle}[750]{Kimahri, gotta watch out for them Ronso!}
    Each Attack does average of 125, count damage compared to average to know if you need to Potion or not, Yevon protect us.
    If you did the above sphere grid already, 6 Attacks will always kill, that's the spirit!
    \begin{itemize}
        \tidusf Attack x5, gotta show him what we got, ya?
        \item \textit{If the Attacks did at least 7 damage over average, time to strike:}
        \begin{itemize}
            \tidusf Attack, gotta finish him off!
        \end{itemize}
        \item \textit{If \tidus\ has less than 178 HP, gotta heal:}
        \begin{itemize}
            \tidusf Potion, heal up brudda!
        \end{itemize}
        \tidusf Attack x1-2, almost done brudda!
    \end{itemize}
\end{battle}
\begin{enumerate}[resume]
    \item \sd, continue running, no time to waste!
\end{enumerate}
\begin{battle}{Garuda, gotta be careful, ya?}
    \begin{itemize}
        \summon{\valefor}
        \valeforf Thunder x6 to build \od, just like charging up for a blitz!
    \end{itemize}
    Guaranteed 1 Power Sphere, gotta get stronger for Yuna.
\end{battle}
\begin{enumerate}[resume]
    \item If you didn't do the above sphere grid yet, do it now, no excuses (only get Cheer if Tidus has 2 levels), ya?
    \item \formation{\tidus}{\yuna}{\lulu} Gotta keep Yuna safe with the right team, just like in Blitzball, ya?
\end{enumerate}
\begin{battle}{Garuda, again? These monsters never quit!}
    \begin{itemize}
        \item Flee using the Escape Command, no shame in running, ya?
    \end{itemize}
\end{battle}
\begin{encounters}
    \begin{itemize}
        \item Dingo: \tidus\ Attack, simple as that, ya?
        \item Condor: \wakka\ Attack, gotta take 'em down!
        \item Water Flan: \lulu\ Thunder, magic's the way to go, ya?
    \end{itemize}
    Guaranteed 1 Power Sphere, Overkill on Dingo gives +1 Power Sphere, gotta get stronger!
\end{encounters}
\begin{enumerate}[resume]
    \item At Besaid Beach \save, talk to the guy in red shorts for 400 Gil, gotta pay up, ya? Then go onto the boat, time to leave Besaid!
\end{enumerate}
\winnp\lossnp\bothnp