\chapter{S.S. Liki, it's a boat!}

\begin{enumerate}
    \item \cs[2:00], gotta walk up to \yuna, protect her ya? \sd, walk back to \wakka, \sd, walk back up to \yuna again, \cs + 4 \skippablefmv[4:20], \sd\ from Sin, Yevon help us!
\end{enumerate}
\begin{battle}[2000]{Sin Fin, nasty monster!}
    \begin{itemize}
        \tidusf Defend, gotta protect the team, ya?
        \switch{\yuna}{\lulu} Gotta get the right player in position, like blitzball, ya?
        \luluf Thunder the Sin Fin, show 'em the power of magic!
        \switch{\kimahri}{\yuna} Time to switch again, like a blitzball play, ya?
        \summon{\valefor} Time to call in the big guns!
        \valeforf Energy Ray \od\ on Sin Fin, that's the spirit!
        \enemyf Move x2 and Spines x2, watch out for those spines!
        \valeforf Thunder the Sin Fin, keep the pressure on!
        \enemyf Spines and Move, dodge 'em like a blitzball!
        \valeforf Thunder the Sin Fin x2, almost there!
        \item \textit{If Sin Fin ain't dead yet, gotta keep fighting:}
        \begin{itemize}
            \enemyf Spines, watch out, brudda!
            \switch{\tidus}{\wakka}
            \wakkaf Attack the Sin Fin, time for a blitzballer's power!
        \end{itemize}
    \end{itemize}
\end{battle}
\begin{enumerate}[resume]
    \item \fmv+\cs[1:40], what's gonna happen next, ya?
\end{enumerate}
\begin{battle}[2000]{Sinspawn Echuilles, little monsters!}
    \begin{itemize}
        \tidusf Cheer x2, gotta pump up the team, just like before a blitzball game!
        \wakkaf Dark Attack, hit 'em where it hurts!
        \tidusf if Str Node Attack x2, otherwise Cheer x2, gotta power up, ya?
        \wakkaf Attack x2, time for some blitzball action!
        \enemyf Blender, that's a nasty move!
        \wakkaf Attack x2, show 'em what we got!
        \tidusf Attack x2, one less if either \tidus\ crits or \wakka\ crits twice, gotta watch out for those criticals!
        \tidusf \od, unleash the fury, ya?
    \end{itemize}
    Check for \textbf{Ice Brand, Ice Ball}, maybe the Al Bhed had somethin' to do with this, ya?
\end{battle}
\begin{enumerate}[resume]
    \item \skippablefmv+\cs[1:30], \sd\ during \tidus's\ monologue, what's he talkin' about, ya?
\end{enumerate}
\wincb\losscb\bothcb\winnpsingle\lossnpsingle\bothnpsingle