\chapter{Luca, Ya?}

\begin{enumerate}
    \item Save data, then go right and up to the next screen, cutscene is two minutes, thirty seconds, ya? No need to save, brudda.
    \item Save data in the locker room, ya? No time for tutorials, no can do! Save data again while mashing R1, then walk down, another save data, ya? Gotta be quick like a blitzball game!
    \item Walk down to the next screen, save data, ya? Whistle cutscene, takes like thirty seconds, ya? Walk right to the next screen, gotta keep movin', like on the blitzball field!
    \item Save data, run to the cafe, ya? Another save data, plus a skippable movie and cutscene, ya? That's one minute and twenty seconds, ya? Save data again, ya?
    \item Run left to the next screen, then left to the docks, ya? Like scoring a goal in blitzball, gotta be quick!
    \item Talk to O'aka on the first docks screen before fightin' those machina, those blasted machines! Gotta do the following shop, ya?
\end{enumerate}
\begin{shop}{3050}
    \begin{itemize}
        \item Sell, gotta get rid of the junk, ya?
        \begin{itemize}
            \item All Weapons and Armor other than Official Ball, Lightning Steel, Thunder Ball, keep the good stuff, ya?
        \end{itemize}
        \item Buy, gotta get some upgrades!
        \begin{itemize}
            \item Stunning Steel, and equip it, ya?
        \end{itemize}
        \item If ya don't got enough gil after sellin' equipment, there are 2 chests with 600 Gil and a Tidal Spear on the same dock as O'aka, sell that spear, ya?
    \end{itemize}
\end{shop}
\begin{enumerate}[resume]
    \item Run north to the next screen, ya? Time to face those blasted machines!
\end{enumerate}
\begin{battle}{Machina - First Two Encounters, Ya?}
    \begin{itemize}
        \tidusf \textit{if Early Haste} Haste Lulu on his first turn, ya? Otherwise, just defend, ya?
        \kimahrif Defend, gotta protect Yuna!
        \luluf Thunder, show 'em the power of Yevon!
    \end{itemize}
\end{battle}
\begin{enumerate}[resume]
    \item Gotta do the Sphere Grid if Tidus has 5 S.Levels, ya? It's like trainin' for a blitzball match!
\end{enumerate}
\begin{battle}{Machina Third Encounter, Ya?}
    \begin{itemize}
        \item \textit{No Early Haste:}
        \begin{itemize}
            \item \textit{First Wave:}
            \begin{itemize}
                \tidusf Attack those machines, ya?
                \kimahrif Attack!
                \luluf Thunder a different Machina, ya?
                \tidusf Attack again!
                \kimahrif \textit{if no crits} Overdrive Seed Cannon, else Attack, ya?
            \end{itemize}
            \item \textit{Second Wave:}
            \begin{itemize}
                \tidusf Defend, brudda!
                \kimahrif Defend, ya?
                \luluf Thunder!
            \end{itemize}
            \item \textit{Third Wave:}
            \begin{itemize}
                \tidusf Attack, ya?
                \kimahrif Attack or use Overdrive Seed Cannon, ya?
                \luluf Thunder a different Machina, ya?
            \end{itemize}
        \end{itemize}
        \item \textit{Early Haste:}
        \begin{itemize}
            \tidusf Haste Lulu, then Defend, ya? Gotta be quick!
            \kimahrif Defend, ya?
            \luluf Thunder!
        \end{itemize}
    \end{itemize}
\end{battle}
\begin{enumerate}[resume]
    \item If anyone's HP is low, use Potions, ya? And if ya had Early Haste, save to restore Tidus's MP, ya? Like resting before the next blitzball match!
    \item Do the below Sphere Grid if Tidus has 5 S.Levels, ya? Gotta get stronger!
    \item Run right, ya?
\end{enumerate}
\begin{battle}[3000]{Oblitzerator, Ya?}
    \begin{itemize}
        \kimahrif Defend, gotta protect Yuna, ya?
        \tidusf \textit{If Early Haste} Haste Lulu, else Defend, ya?
        \luluf Thunder Crane x3, show that machine who's boss!
        \tidusf Use Crane after Lulu's 3rd Thunder, ya?
        \kimahrif Defend!
        \luluf Thunder, ya?
        \tidusf Attack!
    \end{itemize}
    Check for Lightning Steel, Thunder Ball, ya? Good equipment!
\end{battle}
\begin{enumerate}[resume]
    \item Cutscene for two minutes, save data during and after the Blitzball game, ya?
\end{enumerate}
\begin{spheregrid}
    \begin{itemize}
        \tidusf (5 S.Lvl), ya?
        \begin{itemize}
            \item Move down, southeast, southeast, ya?
            \item +1 Strength, Haste, +20 MP, ya?
        \end{itemize}
        \sggraphics{.7}{.4}{graphics/haste}
    \end{itemize}
\end{spheregrid}
\begin{equip}
    \begin{itemize}
        \item \textit{If you got Thunder Ball:}
        \begin{itemize}
            \wakkaf Thunder Ball, time to show 'em what's what!
            \item \textit{If you also got Lightning Steel:}
            \begin{itemize}
                \tidusf Lightning Steel, ya?
            \end{itemize}
        \end{itemize}
    \end{itemize}
\end{equip}
\begin{enumerate}[resume]
    \item Run south for the next two screens, ya? Save data, go up the stairs to the locker room, and save data again, ya?
    \item Go back into the locker room, speak to Wakka, and save data again, ya? Then cutscene for one minute and twenty seconds, ya? Save data after Lulu's scene, and a cutscene for one minute and forty seconds when Auron enters, ya?
\end{enumerate}
\begin{blitzball}
    \begin{itemize}
        \item \textbf{First Half:}
        \begin{itemize}
            \item \textit{If Luca wins the Blitzoff:}
            \begin{itemize}
                \item Triangle, switch the mode to Mark Mode, and then Left Side, ya?
            \end{itemize}
            \item \textit{When you get the ball:}
            \begin{itemize}
                \item Change to Manual A and Normal Mode, ya?
                \item Down some, pass the ball to Tidus, ya?
                \tidusf Swim next to Jassu, pass to Jassu, ya?
                \item Hide behind the Goalie, ya?
                \item If ya aggroed a Goer, Swim Around, ya?
            \end{itemize}
        \end{itemize}
        \item Save data during half time, ya?
        \item \textbf{Second Half:}
        \begin{itemize}
            \item \textit{If Luca wins the Blitzoff:}
            \begin{itemize}
                \item Triangle, switch the mode to Mark Mode, and then Right Side, ya?
            \end{itemize}
            \item \textit{When you get the ball:}
            \begin{itemize}
                \item Pass to Jassu if he doesn't have it, ya?
                \item Swim to the Bottom Middle, ya?
                \item Wait until 2:20, if Abus Aggros then Break, ya?
                \item Swim to the Left, aggro Balgerda, then swim back some, ya?
                \item Pass to Tidus before Balgerda gets in range to block, ya?
                \tidusf Swim close to the Goal and Sphere Shot before anyone is close enough to block, ya?
                \begin{itemize}
                    \item If 1 Defender and 2:49, Sphere Shot over the Defender, ya?
                    \item Otherwise, Break and Sphere Shot, ya?
                    \item If 2 Defenders, Break 1, Sphere Shot, ya?
                \end{itemize}
            \end{itemize}
            \item Save data during Wakka's cutscene, ya?
            \item If ya need to Score or it's 1-1, then do the same as above with Jassu, ya?
            \item Wait until 4:20 then aggro Balgerda, Pass to Wakka, ya?
            \wakkaf swim close and Venom Shot, or Break, Venom Shot, ya?
        \end{itemize}
        \item No tryin' to score in the First Half, ya?
        \item If ya's losing, Change to Mark Mode and lose the game, ya?
    \end{itemize}
\end{blitzball}
\begin{enumerate}[resume]
    \item Save data, don't save, cutscene for one minute, ya?
\end{enumerate}
\begin{battle}{Sahagin Chief, ya?}
    \begin{itemize}
        \item \textit{If no Thunder Ball:}
        \begin{itemize}
            \tidusf Haste Tidus, ya?
            \wakkaf For the first two waves, attack Sahagin C, ya?
            \wakkaf For the third wave, potion Tidus if he has less than 156 HP, otherwise Defend, ya?
        \end{itemize}
        \item \textit{If Thunder Ball:}
        \begin{itemize}
            \tidusf Cheer, ya?
            \wakkaf Attack, ya?
            \tidusf Haste Tidus, ya?
            \tidusf Haste Wakka, ya?
            \item \textit{If also Lightning Steel:}
            \begin{itemize}
                \tidusf Cheer, ya?
            \end{itemize}
        \end{itemize}
        \tidusf Attack!
    \end{itemize}
    Guaranteed 17 Power Spheres, each Overkill is +1 Power Sphere, ya?
\end{battle}
\begin{enumerate}[resume]
    \item Save data, skippable movie, ya? Overkill on Vouivre is +1 Power Sphere, ya?
\end{enumerate}
\begin{battle}[1800]{Garuda, Ya?}
    \begin{itemize}
        \tidusf Haste Auron, ya?
        \auronf Attack x3, show that bird what for!
        \wakkaf Defend, Potion if Tidus has less than 312 HP, gotta keep him healthy!
        \tidusf Attack x1, then Defend, ya?
        \wakkaf Defend, Potion if Auron has less than 202 HP, ya?
        \auronf Attack x3, ya?
        \item No reviving non-Auron party members, ya?
    \end{itemize}
    Guaranteed 2 Power Spheres from this and the Vouivre, ya? Overkill is +1 Power Sphere, ya?
\end{battle}
\begin{enumerate}[resume]
    \item Cutscene plus a skippable movie, one minute, thirty seconds, buffer the movie skip, ya? Don't save, save data at the Auroch scene, ya?
    \item Cutscene is four minutes, fifty seconds, ya? Run north to the hidden chests, pick up Magic and HP Sphere, ya?
    \item Run south and try to speak to Auron while he's walkin' away, ya?
    \item Follow the red arrow to Yuna, save data during guardian scene, ya? Walk to Yuna, cutscene is four minutes, twenty seconds, ya?
\end{enumerate}