\chapter{Mi'ihen Highroad, Ya?}

\begin{enumerate}
\item Gotta move it, brudda! Forced fight, time to focus up. Head up, gotta watch out for those scenes with Maechen, ya know? Power Sphere's comin' from the tutorial, that's a sure ting, plus one if we Overkill, Ya?
\item \formation{\tidus}{\wakka}{\auron}
\item Run away from every fight! No time for dat!
\item Use \yuna's Cure if \tidus\ is in the red, and after every ambush, keep him safe!
\end{enumerate}
\wincb\losscb\bothcb
\begin{enumerate}[resume]
\item {Mi'ihen Skip, Like a Blitzball Pass!}
\begin{itemize}
\item After the Maechen scene, gotta run, run, run! As fast as we can!
\item Go to dat white spot on the ground, left side, before ya see the Man in Blue.
\item Talk to him, and grab the \textbf{Hunter's Spear}, it's worth it, ya?
\item Mash that button and step forward, gotta get over dat cutscene line.
\item Gotta keep walkin' during the cutscene after the teleport, no time to stop!
\end{itemize}
\item Get the \textbf{Hunter's Spear}! No can do if ya fail the skip, it's important!
\item Go right, time to focus up at the Calli scene. Keep movin' forward, brudda! Time to focus up again! Luzzu scene, time to focus up again! Shelinda scene.
\item Next screen, here we go!
\item Gotta find that Al Bhed shop, time to focus up. Walk outta da shop and \cs[5:30]
\item Leave the shop, time to focus up. Time to focus up again on Rin. Head outside.
\end{enumerate}
\begin{battle}{Chocobo Eater, Time to Blitz!}
\begin{itemize}
\tidusf Haste dat Boss, Gotta be quick like a blitz!
\item Defend with everyone, gotta protect each other, bruddas!
\item If someone's low on HP, switch 'em out with someone from the back, no time for heroes!
\end{itemize}
\end{battle}
\begin{enumerate}[resume]
\item Time to focus up!
\item \formation{\tidus}{\wakka}{\auron}
\item Head north, \save. Walk north to the next screen, ya? Walk to da blocked road, time to focus up! Talk to da guard on the right, time to focus up. Head back, time to focus up again. Walk up to da next screen, almost there!
\end{enumerate}