\chapter{Djose, Ya?}

\begin{enumerate}
\item Walk north, ya? If ya don't find a Basilisk by the end of the road, keep fightin' until ya get one. Now or after ya leave Djose Temple, brudda!
\end{enumerate}
\begin{encounters}
\begin{itemize}
\item Basilisk, Ya?
\begin{itemize}
\switch{anyone}{\kimahri}
\kimahrif Gotta use Lancet on that Basilisk, Kimahri! Learn Stone Breath, Ya?
\item Gotta run away, brudda!
\end{itemize}
\item Else Gotta run away!
\end{itemize}
\end{encounters}
\begin{enumerate}[resume]
\item Keep walkin' north, brudda! Stop the timer, and go to the next area!
\item Walk across the bridge to the next area, ya? Stop the timer. Go into the temple, speak to Auron at the door, stop the timer, and go up the stairs.
\end{enumerate}
\begin{trial}
\begin{itemize}
\item Gotta grab the sphere from the left wall, ya?
\item Shove it in the door!
\item Gotta take the sphere from the right wall, brudda!
\item Shove it in the door, ya?
\item Gotta take the sphere from the left wall again!
\item Push that pedestal to the right, brudda!
\item Put the sphere into the far right wall!
\item Take the sphere from the right wall, ya?
\item Place it in the far right wall!
\item Cutscene time, ya?
\item Take the sphere from the far right wall.
\item Reset that puzzle with the far left tile, brudda!
\item Place that sphere into the pedestal, ya?
\item Take the sphere from the pedestal!
\item Put the sphere into the right wall, ya?
\item Take the far right sphere, brudda!
\item Put it into the pedestal, ya?
\item Push the pedestal through the door, brudda!
\item Jump onto the pedestal, ya?
\item Push the second pedestal, and return to the main room!
\item Take the charged sphere from the right wall, ya?
\item Place the charged sphere into the left wall, brudda!
\item Reset the puzzle, ya?
\item Place the two pedestal spheres in the first left and right walls, ya?
\item Go onto the lift in the center.
\item Push all the pedestals in, and walk up the stairs.
\end{itemize}
\end{trial}
\begin{enumerate}[resume]
\item Talk to Auron, and wait for him, brudda. Stop the timer, try to leave, stop the timer, and name Ixion!
\item Speak to Auron, enter the temple, and go to the left room. Speak to the priest, and stop the timer. Exit the temple, and stop the timer, brudda!
\item Go left, pick up 4000 Gil, cross the bridge, stop the timer, exit, stop the timer, and go up to Moonflow, ya?
\end{enumerate}
\wincb\losscb\bothcb