\chapter{Moonflow, Ya?}

\begin{enumerate}
\item Set up the team as Tidus, Kimahri, and Auron, ya?
\item Walk north, and stop the timer on that Kimahri scene, brudda!
\item Before Belgemine, go right into the alcove and pick up 3 Lv. 1 Key Spheres, ya?
\item Walk north, stop the timer, walk left, stop the timer, walk left past two screens, and stop the timer, brudda!
\end{enumerate}
\begin{spheregrid}
\begin{itemize}
\wakkaf (7 S.Lvl), Ya? If ya don't have enough, skip this grid entirely, brudda!
\begin{itemize}
\item Move down twice and right to Silence Attack, ya?
\item Gotta get that +2 Strength, brudda!
\end{itemize}
\sggraphics{.7}{.4}{graphics/Wakka_Grid}
\end{itemize}
\end{spheregrid}
\begin{equip}
\begin{itemize}
\item \textit{If ya don't have the Thunder Ball, ya?}
\begin{itemize}
\wakkaf Gotta equip the Official Ball, brudda!
\end{itemize}
\item \textit{If ya had the Lighting Steel, brudda:}
\begin{itemize}
\tidusf Gotta equip the Stunning Steel, ya?
\end{itemize}
\end{itemize}
\end{equip}
\begin{enumerate}[resume]
\item Potion or Cure Tidus if he got hurt, brudda. Walk right and use the second option to ride the shoopuf, stop the timer!
\end{enumerate}
\begin{battle}[4000]{Extractor}
\begin{itemize}
\tidusf Haste himself, ya?
\wakkaf If anyone's HP is less than 216, use a Hi-Potion, otherwise Attack, brudda!
\tidusf Attack that Extractor until you make it Slow, ya?
\item \textit{If Extractor ain't Slowed when it Rises, ya?}
\begin{itemize}
\wakkaf Time for my Overdrive! Thunder Reels!
\end{itemize}
\tidusf Haste Wakka, ya?
\item \textit{If ya got Lightning Steel, brudda:}
\begin{itemize}
\tidusf Cheer once, ya?
\tidusf Equip Lightning Steel, ya?
\end{itemize}
\textit{Else:}
\begin{itemize}
\tidusf Cheer four times, ya?
\tidusf Equip Bruddahood, brudda!
\end{itemize}
\tidusf Attack, ya?
\end{itemize}
\end{battle}
\begin{enumerate}[resume]
\item Stop the timer, walk left to the next area, walk left and talk to Rikku, and stop the timer, ya? That Al Bhed...
\item Walk up to the forced battle, brudda!
\end{enumerate}
\begin{battle}{Rikku Tutorial}
\begin{itemize}
\item Mash through the tutorial, brudda!
\rikkuf Gotta Steal from that Treasure Chest, ya?
\ifthenelse{\equal{\blitzresult}{win}}{%
\item \textit{If ya have less than 34 Power Spheres, ya?}
}{\ifthenelse{\equal{\blitzresult}{both}}{%
\item \textit{If ya have less than 34 (or 35 on a loss) Power Spheres, brudda:}
}{%
\item \textit{If ya have less than 35 Power Spheres, brudda:}
}}
\begin{itemize}
\rikkuf Time for an Overdrive! Two Ability Spheres, ya?
\end{itemize}
\item \textit{Else:}
\begin{itemize}
\rikkuf Time for an Overdrive! Two Potions or Hi-Potions, ya?
\rikkuf Defend, brudda!
\item Gotta run away from this fight!
\end{itemize}
\end{itemize}
Ya get +2 Power Spheres when ya do that Ability Sphere Mix, brudda!
\end{battle}
\begin{spheregrid}
\begin{itemize}
\tidusf (4 S.Lvl), ya?
\begin{itemize}
\item Move right then up, ya?
\item Get Strength +1, HP +200, and Agility +2, brudda!
\end{itemize}
\sggraphics{.7}{.4}{graphics/Tidus_post_gui}
\end{itemize}
\end{spheregrid}
\begin{enumerate}[resume]
\item Gotta Auto-Sort the items, ya?
\item Heal everyone with Potions (use 'em all if ya can, gotta free up that first inventory slot), brudda!
\item If your first inventory slot ain't empty: Manual Sort, select what's in the first slot, scroll down a page with R2, and put it there, ya?
\item Gotta set up the team with Tidus, Wakka, and Auron, brudda!
\item Walk north to the next area, ya?
\end{enumerate}