\chapter{Thunder Plains, Brudda!}

\begin{enumerate}
    \item Head north, dodge that lightning, ya? Just like dodging blitzballs from the Al Bhed! Flee from all the battles, no time to waste!
\end{enumerate}
\begin{enumerate}[resume]
    \item \sd\ when we see the Al Bhed shop. Walk inside when Rikku... Rikku?!... begs to go. Probably full of machina junk, ya?
\end{enumerate}
\begin{shop}{1200}
    Buy:
    \begin{itemize}
        \ifthenelse{\equal{\blitzresult}{win}}{%
        }{\ifthenelse{\equal{\blitzresult}{both}}{%
            \item If \blitzloss\  Baroque Sword (Equip), ya?
        }{%
            \item If we lost the blitz game a bit, buy Baroque Sword (Equip)
        }}
        \item 3 Phoenix Downs, gotta keep Yuna safe, ya?
        \ifthenelse{\equal{\blitzresult}{win}}{%
            \item 3 Grenades, those Al Bhed grenades are nasty!
        }{\ifthenelse{\equal{\blitzresult}{both}}{%
            \item 3 Grenades, +1 if we lost a lil' in the blitz tourney
        }{%
            \item 4 Grenades, just in case, ya?
        }}
        , +1 if we need more Speed Spheres (need 15 Speed Spheres for the rest of the run, ya?).
    \end{itemize}
\end{shop}
\begin{enumerate}[resume]
    \item Walk into the shop thingy, \cs[2:00]
    \item Talk to Auron, then Rikku...Rikku?!, \sd.
    \item Gotta grab the \textbf{Yellow Shield} outside the shop, ya? It's on the ground.
\end{enumerate}
\begin{equip}
    \begin{itemize}
        \tidusf Yellow Shield for Tidus, ya?
    \end{itemize}
\end{equip}
\begin{enumerate}[resume]
    \item Try to finish up in Thunder Plains with the Light Curtain, ya?
\end{enumerate}
\begin{encounters}
    Iron Giants always go for the person with the least HP, so make sure everyone's HP is higher than Rikku's...Rikku?!
    \begin{itemize}
        \item Iron Giant + 2 Buers, if we bought an extra grenade for Speed Spheres (only do this once, ya?):
        \begin{itemize}
            \switch{\tidus}{\rikku}
            \rikkuf Rikku...Rikku?! throws a Grenade, ya?
            \wakkaf Wakka defends, gotta protect Yuna!
            \auronf Auron defends too, ya?
            \enemyf They attack Rikku...Rikku?!
            \switch{\wakka}{\tidus}
            \item Gotta flee, brudda!
        \end{itemize}
        \item Just an Iron Giant (only do this once):
        \begin{itemize}
            \tidusf Tidus defends, ya?
            \switch{\wakka}{\rikku}
            \rikkuf Rikku...Rikku?! tries to steal a Light Curtain, ya?
            \auronf Auron defends, like a blitzball goalie!
            \enemyf Attacks Rikku...Rikku?!
            \item Gotta run, brudda!
        \end{itemize}
        \blitzballdetermination[true]{}{\item A Larva, eh? Gotta steal a Lunar Curtain, ya?}
    \end{itemize}
\end{encounters}
\begin{enumerate}[resume]
    \item Exit the screen, head north, near the exit \sd, \cs[3:10]
\end{enumerate}