\chapter{Macalania Woods, Ya?}

\begin{enumerate}
    \item \sd, head north, \sd, \save. Gotta keep Yuna safe, ya?
    \item \formation{\tidus}{\rikku}{\auron}
    \item Heal Tidus if he's below 404 HP, ya? Can't let the star blitzball player get hurt!
    \item Charge Rikku's...Rikku's?!... \od, and steal at least one of each thing, ya? Gotta get those items!
\end{enumerate}
\begin{encounters}
    \begin{itemize}
        \item Chimera? Steal an Arctic Wind, then FLEE!
        \item Blue Elemental? Steal Fish Scale x2, then run, ya?
        \item Anything else? No time, just Flee!
    \end{itemize}
\end{encounters}
\begin{enumerate}[resume]
    \item Once Rikku's...Rikku's?!... got \od\ and we got at least 1 Arctic Wind and 1 Fish Scale, \formation{\tidus}{\kimahri}{\auron}
    \item Follow the path, \sd\ twice.
    \item Catch that butterfly near the exit to avoid those battles, ya?
    \formation{\tidus}{\kimahri}{\auron}
    \item \save, talk to O'aka, ask about weapons ("Got any weapons?"), then exit the shop. Say it's too pricey ("Too pricey."), then ask again ("Got any weapons?")
\end{enumerate}
\begin{shop}{11550}
    \begin{itemize}
        \item Sell: Stunning Steel, Buckler, Hunter Spear, anything else to get over 11550 Gil, ya?
        \item Buy:
        \begin{itemize}
            \item Sonic Steel, Equip it on Tidus, ya?
            \item Shimmering Blade, Equip it on Auron, ya?
        \end{itemize}
    \end{itemize}
\end{shop}
\begin{enumerate}[resume]
    \item Run up ahead, \sd. Go into the hidden path, walk to Auron, \sd
\end{enumerate}
\begin{battle}[12000]{Spherimorph, the elemental blitzball!}
    \begin{itemize}
        \tidusf Tidus defends, ya?
        \switch{\tidus}{\yuna}
        \yunaf Yuna defends, gotta protect her!
        \kimahrif Kimahri defends, like a good Guardian, ya?
        \switch{\auron}{\rikku}
        \rikkuf Rikku...Rikku?! uses a Grenade, and check what element it is, ya?
        \yunaf Yuna defends, ya?
        \rikkuf Rikku's...Rikku's?!... \od, HP Sphere with:
        \begin{itemize}
            \item Fire? Use Arctic Wind, ya?
            \item Ice? Bomb Core, ya?
            \item Water? Lightning Marble, ya?
            \item Thunder? Fish Scale, ya?
        \end{itemize}
        \item \textit{If we're outta stuff:}
        \begin{itemize}
            \switch{\rikku}{\lulu}
            \luluf Lulu uses the opposite spell of what Spherimorph used, ya?
            \kimahrif Kimahri attacks, check the element, ya?
            \switch{\yuna}{\rikku}
            \rikkuf Rikku's...Rikku's?!... \od, ya?
        \end{itemize}
    \end{itemize}
    Tidus, Yuna, Kimahri, and Rikku...Rikku?!... all need AP, ya?
\end{battle}
\begin{enumerate}[resume]
    \item \cs[1:50], \sd, \sd
\end{enumerate}
\begin{spheregrid}
    \begin{itemize}
        \rikkuf (1 S.Lvl), Rikku...Rikku?!... gotta move, ya?
        \begin{itemize}
            \item Move down, ya? $\downarrow$
            \item Agi+3, nice!
        \end{itemize}
        \sggraphics{.7}{.4}{graphics/macalaniarikku}
        \kimahrif (15 S.Lvl), Kimahri's turn, ya?
        \begin{itemize}
            \item Move down six times, ya? $\downarrow x6$ (or Hold $\downarrow$), next to that Lv. 1 Lock, ya?
            \item Level 1 Key Sphere, ya?
            \item Move left four times $\leftarrow x4$ (or Hold $\leftarrow$), ya?
            \item Another Level 1 Key Sphere, ya?
            \blitzballdetermination[true]{%
                \item Move up twice and left once $\uparrow\uparrow\leftarrow$, like a blitzball play, ya?
            }{%
                \item Move up twice and down once $\uparrow\uparrow\downarrow$, ya?
                \item HP+200, HP+200, nice HP boost!
                \item Move left, ya? $\leftarrow$
            }
            \item Steal, and Use, ya?
        \end{itemize}
        \ifthenelse{\equal{\blitzresult}{win}}{%
            \sggraphics{.7}{.4}{graphics/Kimahri_post_spheremorph}
        }{%
            \ifthenelse{\equal{\blitzresult}{both}}{%
            \sggraphics{.7}{.4}{graphics/Kimahri_post_spheremorph_loss}
        }{%
            \sggraphics{.7}{.4}{graphics/Kimahri_post_spheremorph_loss}
        }}
    \end{itemize}
\end{spheregrid}
\begin{enumerate}[resume]
    \item \formation{\tidus}{\lulu}{\kimahri}
    \ifthenelse{\equal{\blitzresult}{both}}{%
        \item If we lost at blitzball and don't have a Light Curtain, use a Mega-Potion, ya?
    }{%
        \ifthenelse{\equal{\blitzresult}{loss}}{%
        \item If we don't have a Light Curtain, use a Mega-Potion, ya?
    }{}}
    \item Talk to Auron on the way out, then leave, ya?
\end{enumerate}
\winnp