\chapter{Lake Macalania, ya? Like a Blitzball Arena, Brudda!}

\begin{enumerate}
    \item Run up and \sd, like runnin' up the field, ya?
\end{enumerate}
\begin{battle}[16000]{Crawler, huh? Sounds like Al Bhed Machina}
    \begin{itemize}
        \switch{\tidus}{\rikku}
        \rikkuf Rikku's...Rikku's?!... gonna mix a Lightning Marble with a Negator (1\,000 HP), ya?
        \rikkuf Then mix a Lightning Marble with the Crawler, gotta stop that Al Bhed junk, ya?
        \kimahrif Kimahri's gonna hit that Crawler with a Lightning Marble, show 'em Ronso power!
        \luluf Lulu uses a Phoenix Down on Rikku...Rikku?!, gotta keep her alive!
        \rikkuf Then another Lightning Marble on the Crawler, Al Bhed are always makin' trouble, ya?
        \ifthenelse{\equal{\blitzresult}{win}}{%
            \switch{\lulu}{\yuna}
            \yunaf Yuna uses Mega Phoenix, send those baddies to the Farplane!
            \switch{\yuna}{\tidus}
            \tidusf Tidus equips Bruddahood, time to get serious, ya?
        }{%
            \ifthenelse{\equal{\blitzresult}{loss}}{%
                \kimahrif If we need a Lunar Curtain, Kimahri steals from the Crawler, else defends! Gotta protect us!
                \switch{\lulu}{\yuna}
                \yunaf If two people are dead, Mega Phoenix, else Phoenix Down Rikku...Rikku?!, keepin' us goin'
                \switch{\yuna}{\tidus}
                \tidusf If Kimahri's down, Phoenix Down him, otherwise equip Bruddahood! Gotta keep the team alive!
            }{%
                \kimahrif If we lost blitz and need a Lunar Curtain, Kimahri steals from the Crawler, else defend! Gotta watch out!
                \switch{\lulu}{\yuna}
                \yunaf If two people are dead, Mega Phoenix, else Phoenix Down Rikku...Rikku?!, Yuna's prayin' to Yevon!
                \switch{\yuna}{\tidus}
                \tidusf If Kimahri's dead, Phoenix Down him, otherwise equip Bruddahood! Gotta be ready!
            }}
        \rikkuf Rikku's...Rikku's?!... \od\ for a Lv. 2 Key Sphere and a Lightning Marble! Gotta get those goodies!
    \end{itemize}
    Tidus, Yuna, Lulu and Kimahri all need AP! Gotta get stronger for the pilgrimage!
\end{battle}
\begin{spheregrid}
    \begin{itemize}
        \kimahrif (12 S.Lvl), gotta make Kimahri stronger, ya?
        \begin{itemize}
            \item Move down four times on the Luck node, ya? $\downarrow\downarrow\downarrow\downarrow$ Gotta get lucky like winning the Blitzball tourney, ya?
            \item HP + 200, Agi+4, Gotta make sure he's ready to defend Yuna!
        \end{itemize}
        \sggraphics{.7}{.4}{graphics/macalania_kimahri}
        \tidusf (22 S.Lvl), Tidus needs to bulk up, ya?
        \begin{itemize}
            \item Level 2 Key Sphere, just like gettin' the Jecht Shot, ya?
            \item Move right then up, gotta move fast like on the blitzball field, ya? $\rightarrow\uparrow$
            \item Str + 4, Gotta get stronger for Yuna, ya?
            \item Move up twice, ya? $\uparrow\uparrow$, Gotta get up there like the Aurochs tryin' to win, ya?
            \item HP+200, Gotta keep Tidus alive, ya?
            \item Move right twice then up, Gotta move fast, ya? $\rightarrow\rightarrow\uparrow$
            \item HP+200, Str+4, Agi+2, Time to get ready for Sin, ya?
            \item \blitzballdetermination[true]{%
                \item Move right, gotta move right on the blitzball field, ya? $\rightarrow$
                \item Use a Strength Sphere and activate it, like usin' the Jecht Shot, ya?
                \item Move up then left twice, or northwest twice, gotta go left sometimes, ya? $\uparrow\leftarrow\leftarrow$ or $\nwarrow\nwarrow$
            }{%
                \item Move up then left, ya? Gotta get up, ya? $\uparrow\leftarrow$
            }
            \item HP+200, Str+4, Agi+2, Time to be ready for anything, ya?
            \item Move left, gotta go left, ya? $\leftarrow$
            \item Str+4, Gotta get stronger, ya?
        \end{itemize}
        \ifthenelse{\equal{\blitzresult}{win}}{%
            \sggraphics{.7}{.4}{graphics/Tidus_post_crawler}
        }{\ifthenelse{\equal{\blitzresult}{both}}{%
            \sggraphics{.7}{.4}{graphics/Tidus_post_crawler}
        }{%
            \sggraphics{.7}{.4}{graphics/Tidus_post_crawler_loss}
        }}
    \end{itemize}
\end{spheregrid}
\begin{enumerate}[resume]
    \item \sd, \cs[0:40], head to the next screen, time to keep movin' for Yuna, ya?
    \item Head to the Temple, \sd. \save, Gotta save Yuna, ya?
    \wincb
    \item Jyscal Skip (Ignore if playing with Cutscene Remover): No time for cutscenes, gotta get to Yuna, ya?
    \begin{itemize}
        \item Speak to Tromell for the \textbf{Shell Targe}, maybe it'll protect us from Sin, ya?
        \item Walk into the wall to the right of Tromell, these temples are tricky, ya?
        \item Move slightly right, turn around and talk to Tromell while moving right, Tromell's confused, ya?
        \item If it works, walk forward while mashin' Shelinda's dialogue, Shelinda won't stop talkin', ya?
        \item When dialogue finishes, walk up the stairs, push the man, and go through, gotta be sneaky, ya?
        \item If Shelinda ain't sayin' nothin', talk to one of the musicians, maybe they know somethin', ya?
    \end{itemize}
    \item \sd, walk to the Fayth room, \cs[2:10], gotta protect Yuna in here, ya?
\end{enumerate}
\begin{battle}[3000]{Seymour, that Maester, huh?}
    \begin{itemize}
        \tidusf Haste Tidus, Tidus needs to be quick, like a blitzball player!
        \yunaf Change Weapon to Staff, Yuna's gonna use her faith, ya?
        \kimahrif Kimahri uses \od\ Stone Breath, Kimahri's gonna show 'em, ya?
        \tidusf Talk to Seymour, gotta get some answers from him, ya?
        \switch{\yuna}{\auron}
        \auronf Defend, gotta protect Yuna, ya?
        \enemyf Seymour uses Blizzara, Seymour's makin' it cold, ya?
        \ifthenelse{\equal{\blitzresult}{win}}{%
            \tidusf Defend, gotta protect everyone, ya?
        }{%
            \ifthenelse{\equal{\blitzresult}{loss}}{%
                \tidusf Cheer, cheer up the team, ya?
            }{%
                \tidusf if we lost blitz, cheer, else defend, time to cheer or defend, ya?
            }}
        \tidusf Attack, Gotta take 'em down, ya?
    \end{itemize}
\end{battle}
\begin{battle}[18000]{Anima, that summon is scary, ya?}
    \begin{itemize}
        \blitzballdetermination[true]{%
            \kimahrif Defend, Kimahri's protectin', ya?
            \auronf Defend, gotta protect Yuna, ya?
            \switch{\tidus}{\wakka}
            \wakkaf Change Weapon to anything, I'm just protectin', ya?
            \enemyf Anima uses Pain, gonna hurt, ya?
            \switch{first survivor}{\tidus}
            \tidusf Attack x4, Tidus is goin' for it, ya?
            \switch{second survivor}{\rikku}
            \rikkuf Steal x2, Rikku's...Rikku's?!... stealin' stuff, ya?
        }{%
            \kimahrif Hit Anima with a Lightning Marble, Kimahri's gonna get 'em, ya?
            \switch{\auron}{\rikku}
            \rikkuf Rikku's...Rikku's?!... mixin' with a Lightning Marble, ya?
            \switch{\tidus}{\wakka}
            \wakkaf Change Weapon to anything, I'm just tryin' to help, ya?
            \enemyf Anima uses Pain, gonna hurt us, ya?
            \switch{first survivor}{\tidus}
            \tidusf Attack x4, Tidus is attackin', ya?
            \switch{second survivor}{\rikku\ or \kimahri}
            \item Rikku or Kimahri: Steal, gotta steal from 'em, ya?
        }
        \item \textit{If Tidus Misses:}, Tidus missed, ya?
        \begin{itemize}
            \item On Tidus' 4th turn, switch him for Lulu, Lulu's gonna come in, ya?
            \luluf Lulu uses Phoenix Down on a dead character, Lulu's gonna revive, ya?
            \enemyf Anima uses Pain, still hurtin', ya?
            \switch{first survivor}{\tidus}
            \item Continue the fight like normal, gotta keep goin', ya?
        \end{itemize}
    \end{itemize}
\end{battle}
\begin{battle}[6000]{Seymour again? He's persistent, ya?}
    \begin{itemize}
        \tidusf Phoenix Down Rikku...Rikku?!, if she died before Multi-Thundara, gotta revive her, ya?
        \blitzballdetermination[true]{\tidusf Change Weapon to Sonic Steel, like usin' a Jecht Shot, ya?}{}
        \item Anyone: Defend until Multi-Thundara, gotta brace for it, ya?
        \enemyf Seymour uses Multi-Thundara, gonna blast us, ya?
        \tidusf Attack x2, Tidus's gonna strike, ya?
    \end{itemize}
    Tidus and Yuna need AP! Gotta make 'em stronger!
\end{battle}
\begin{enumerate}[resume]
    \item Name Shiva, gotta name the Aeon, ya?
\end{enumerate}
\begin{spheregrid}
    \begin{itemize}
        \tidusf, Tidus needs to get better, ya?
        \begin{itemize}
            \item Move left four times, gotta move left on the sphere grid, ya? $\leftarrow\leftarrow\leftarrow\leftarrow$
            \item HP+200, Str+4, gotta get health and strength, ya?
            \item Move left, gotta move left, ya? $\leftarrow$
            \item Agi+2, gotta get agility up, ya?
        \end{itemize}
        \sggraphics{.7}{.4}{graphics/Tidus_Post_Seymour}
    \end{itemize}
\end{spheregrid}
\begin{enumerate}[resume]
    \item We need 21 Power Spheres and 10 Speed Spheres \textbf{at this point} to be done farmin' 'em, time to get those spheres!
    \item \formation{\rikku}{\tidus}{\kimahri}, Gotta set up the team, ya?
    \ifthenelse{\equal{\blitzresult}{win}}{}{
        \ifthenelse{\equal{\blitzresult}{both}}{
            \item \textit{If you lost blitz:}, If we lost blitz, ya?
        }{}
        \begin{equip}
            \begin{itemize}
                \tidusf Equip Sonic Steel, gotta use the Sonic Steel, ya?
            \end{itemize}
        \end{equip}
    }
    \item \save, exit the Fayth room. Make sure to save \textbf{after} the sphere grid, otherwise we'll die to Wendigo!
\end{enumerate}
\begin{trial}
    \begin{itemize}
        \item Slide the pedestal to the right, gotta move it right, ya?
        \item Take the sphere from the right wall, place it in the pedestal, gotta put it in, ya?
        \item Push the pedestal up, Gotta push it up, ya?
        \item Take the Glyph sphere from the middle pillar, grab the sphere, ya?
        \item Go downstairs and push the pedestal to the right, push it again, ya?
        \item Place the Glyph sphere in the far left slot in the wall, gotta put it on the wall, ya?
        \item Go upstairs, pick up the new sphere, gotta get another one, ya?
        \item Go downstairs, place the sphere in the pillar, gotta put it in the pillar, ya?
        \item Go upstairs, take the sphere at the top of the slope, time to climb the slope, ya?
        \item Place it in the last pillar, last one, ya?
    \end{itemize}
\end{trial}
\begin{enumerate}[resume]
    \item Go to the temple entrance, \sd, gotta save Yuna, ya?
    \item Move south and go down the left path, take the left path brudda, ya?
    \blitzballdetermination[true]{%
        \item Try not to get caught by the Guados chasin' ya, if you get caught, flee! Like dodgin' defenders in blitzball!
    }{%
        \item Intentionally get caught by a Guado, kill the enemies to get AP on Tidus, gotta fight the Guados, ya?
        \begin{encounters}
            \begin{itemize}
                \tidusf Tidus attacks a Guado, then any surviving enemies, ya?
                \rikkuf Rikku uses a Silence Grenade, Rikku's gonna silence 'em, ya?
                \kimahrif Kimahri defends, protectin', ya?
            \end{itemize}
        \end{encounters}
    }
\end{enumerate}
\bothcb
\blitzballdetermination{}{
    \begin{spheregrid}
        \begin{itemize}
            \tidusf, Gotta make Tidus stronger, ya?
            \begin{itemize}
                \item Move down twice, or just hold down, ya? $\downarrow\downarrow$ (or $\downarrow$)
                \item Str+4, time to get some strength, ya?
            \end{itemize}
        \end{itemize}
        \sggraphics{.7}{.4}{graphics/tidus_bikanel}
    \end{spheregrid}
}
\begin{battle}[18000]{Wendigo, that beast is tough, ya?}
    \begin{itemize}
        \tidusf Haste Tidus, gotta be fast, ya?
        \tidusf Switch to Bruddahood, Gotta use the Bruddahood, ya?
        \tidusf Attack Guado B (Top One), gotta attack that Guado, ya?
        \item \textit{If there's a Light Curtain:}, If there's a light curtain, ya?
        \begin{itemize}
            \rikkuf Rikku...Rikku?!... uses Light Curtain on Tidus, ya?
        \end{itemize}
        \textit{Else:}, If not, ya?
        \begin{itemize}
            \switch{\rikku}{\auron}
            \auronf Auron uses Power Break on Wendigo, gonna break his power, ya?
            \switch{\auron}{\rikku} Switch back to Rikku on his next turn, ya?
        \end{itemize}
        \tidusf Use Spiral Cut on Wendigo, then attack it until it's dead!
        \kimahrif Steal from Guado if everyone's at full HP, else switch to Lulu, ya?
        \luluf Elixir on Tidus / Phoenix Down on a dead character / Defend, Lulu's gotta heal, ya?
        \rikkuf Elixir on Tidus / Phoenix Down on a dead character / Steal from Guado / Defend, Rikku's stealin', ya?
        \item After Wendigo is dead:, After the Wendigo's gone, ya?
        \begin{itemize}
            \switch{anyone}{\yuna}
            \yunaf Defend, Yuna's gonna defend, ya?
            \switch{anyone}{\tidus}
            \tidusf Attack the Guado, ya?
        \end{itemize}
    \end{itemize}
    Yuna, Tidus need AP. Helpful if Lulu gets it too, ya?
    Guaranteed 2 Power Spheres, +2 more if the rare drop from Wendigo happens, ya?
\end{battle}
\begin{enumerate}[resume]
    \item Run up to Rikku...Rikku?!, \sd, walk up to Yuna, \sd, \save, run past Kimahri and go to the hidden area to grab the \pickup{Level 2 Key Sphere}, gotta run to Rikku and Yuna, ya?
    \item Run up to Auron and talk to him, \sd, walk back, \cs+\skippablefmv[1:00], (press Start immediately after skip), \sd\ in the Dream Sequence, Time to talk to Auron brudda, ya?
\end{enumerate}
\lossnp\bothcb\bothnpsingle