\chapter{Bikanel Desert, ya? Hot like a blitzball match in Kilika!}

\begin{enumerate}
    \item Walk up ahead, \sd, keep walkin'.
\end{enumerate}
\begin{battle}{Zu, that bird's huge, ya?}
    \begin{itemize}
        \tidusf Tidus attacks, ya?
        \enemyf It attacks back!
        \tidusf Tidus equips Sonic Steel, like the Jecht Shot, ya?
        \tidusf Defend until Lulu shows up, gotta wait for backup, ya?
        \auronf Auron defends too, ya?
        \item Gotta flee!
    \end{itemize}
\end{battle}
\begin{enumerate}[resume]
    \item \sd, then run up to Wakka, \sd. Go left to the next screen, go right to Kimahri, \sd. Run back then up to Rikku...Rikku?!, \sd, \save
    \item Need 6 (4 if we still got 2 Bomb Cores) Silence Grenades, Sleeping Powders, or Smoke Bombs. Gotta get ready for the Al Bhed, ya?
    \item If Rikku...Rikku?!... needs her \od, charge it on a Zu or a Sand Worm (Escape with the others). Gotta get her ready, ya?
\end{enumerate}
\begin{enumerate}[resume]
    \item Keep goin' along the path. On the next screen, go northwest towards the save sphere, take the shortcut on the left. Go up to the next screen and fight those Sandragoras. Top right sinkhole with a chest, then the end of the path up and to the left, then go up and \sd
\end{enumerate}
\begin{encounters}
    \begin{itemize}
        \item Steal (preferably Sleeping Powders) and maybe use items on these enemies, ya?
        \begin{itemize}
            \item Sand Wolf, steal Sleeping Powders x2, drops 2 Power Spheres, ya?
            \item Zu, steal Smoke Bomb x3 (don't try to kill 'em), ya?
            \item Alcyone, steal Smoke Bomb x1, drops 2 Speed Spheres, ya?
            \item Mushussu, drops 1 Power Sphere (don't steal), ya?
        \end{itemize}
        \item \textit{If we get the first move:}
        \begin{itemize}
            \tidusf Tidus defends, ya?
            \rikkuf Rikku...Rikku?!... steals or uses a Smoke Bomb / Silence Grenade / Sleeping Powder, ya?
            \luluf Lulu defends, ya?
            \item Then, flee!
        \end{itemize}
        \item \textit{If it's neutral:}
        \begin{itemize}
            \switch{\tidus}{\kimahri}
            \kimahrif Kimahri steals, ya?
            \rikkuf Rikku...Rikku?!... switches for Tidus or uses a Smoke Bomb / Silence Grenade / Sleeping Powder, ya?
            \item Then flee, ya?
        \end{itemize}
        \item \textit{If we get ambushed:} Flee!
    \end{itemize}
\end{encounters}
\begin{battle}{Sandragora, those are ugly, ya?}
    \begin{itemize}
        \switch{\tidus}{\auron}
        \auronf Auron uses \od\ Shooting Star (Triangle, O, Square, X, $\leftarrow, \rightarrow$, X), show 'em Ronso power!
    \end{itemize}
\end{battle}
\begin{enumerate}[resume]
    \item At the bottom of the pit, grab the \pickup{Teleport Spheres}, gonna need these, ya?
\end{enumerate}
\blitzballdetermination{
    \begin{spheregrid}
        \begin{itemize}
            \tidusf Gotta get Tidus stronger, ya?
            \begin{itemize}
                \item Move down twice (or just hold down), ya? $\downarrow\downarrow$ (or $\downarrow$)
                \item Str+4, time for strength, ya?
            \end{itemize}
        \end{itemize}
        \sggraphics{.7}{.4}{graphics/tidus_bikanel}
    \end{spheregrid}
}{}
\begin{enumerate}[resume]
    \blitzballdetermination[true]{%
        \item \formation{\tidus}{\lulu}{\auron}, gonna set up the team, ya?
    }{%
        \item \formation{\tidus}{\rikku}{\auron}, gonna set up the team, ya?
    }
    \item We need 22 Power Spheres and 10 Speed Spheres \textbf{at this point}, time to farm, ya?
    \item Sandragora Skip, ya?
    \begin{itemize}
        \item Go near the Sandragora pit blockin' the way to Home, ya?
        \item Run North into the wall just right of the pit 'til Tidus is in the pit, ya?
        \item Let Rikku...Rikku?!... push ya (don't move til she goes past), ya?
        \item Go north and enter Home, ya?
        \item If Rikku's stuck runnin' East, walk South to start the Sandragora fight, ya?
        \item If we fight 'em, flee and try again, ya?
    \end{itemize}
\end{enumerate}
\bothcb\winnpsingle\lossnpsingle