\chapter{Home, ya? I don't trust the Al Bhed!}

\begin{enumerate}
    \item Go into the door, ya? \sd
\end{enumerate}
\begin{battle}{Bombs, gotta watch out for those}
    \begin{itemize}
        \tidusf Haste Tidus, Gotta make Tidus faster, ya?
        \blitzballdetermination[true]{%
            \tidusf Attack each of 'em, startin' with that Guado! Tidus gotta focus, ya?
            \item Others, defend! Protect Yuna, ya?
        }{%
            \tidusf Attack the Guado, Gotta take 'em down, ya?
            \rikkuf Rikku...Rikku?!... throws a Grenade, ya?
            \tidusf Attack the Bombs x2, Gotta blow 'em up, ya?
            \auronf Auron defends, ya?
            \item \textit{If Kimahri doesn't have \od:}, Gotta check if Kimahri's ready, ya?
            \begin{itemize}
                \switch{anyone}{\kimahri}
                \kimahrif Kimahri uses Lancet on a Bomb, learn some skills!
                \switch{anyone}{\tidus}
            \end{itemize}
            \tidusf Attack the Bomb, Last one, ya?
        }
    \end{itemize}
    Guaranteed 6 Power Spheres, Sweet!
\end{battle}
\begin{enumerate}[resume]
    \item \formation{\tidus}{\lulu}{\auron}, Gotta set up the team, ya?
    \item Follow the others, \sd, Gotta keep up with Yuna, ya?
\end{enumerate}
\begin{battle}{Dual Horn, That thing looks mean, ya?}
    \begin{itemize}
        \switch{anyone}{\kimahri}
        \blitzballdetermination[true]{%
            \kimahrif Lancet Dual Horn (Fire Breath) if he doesn't have \od, learn it!
        }{}
        \kimahrif Kimahri uses \od\ Stone Breath, Show 'em Ronso power!
    \end{itemize}
\end{battle}
\begin{enumerate}[resume]
    \item Go down the stairs, ya? Once the camera flips, \formation{\tidus}{\lulu}{\auron}
    \blitzballdetermination[true]{}{%
        \item Go back up the stairs into the left door, gotta go back, ya?
        \item Gonna fight another Dual Horn!
        \begin{battle}{Dual Horns, Two of 'em, ya?}
            \begin{itemize}
                \switch{anyone}{\kimahri}
                \kimahrif Kimahri uses Lancet on a Dual Horn (Fire Breath), learn it, ya?
                \kimahrif Kimahri uses \od\ Stone Breath, Show 'em Ronso power!
            \end{itemize}
        \end{battle}
        \item \formation{\tidus}{\lulu}{\auron}, Gotta set up the team, ya?
        \item Open the right chest for a \textbf{Friend Sphere}, with the codes: Bottom Middle (up x2), Middle Right (up x4), Middle (down x4), exit and go down the stairs again!
    }
    \item Go left into the door, \cs[0:50], Time to see what's goin' on, ya?
\end{enumerate}
\begin{battle}{Chimera, Another one, ya?}
    \begin{itemize}
        \switch{anyone}{\kimahri}
        \kimahrif Kimahri uses Lancet on Chimera (Aqua Breath), Learn from it, ya?
        \kimahrif Kimahri uses \od\ Stone Breath, Show 'em Ronso power!
    \end{itemize}
\end{battle}
\begin{enumerate}[resume]
    \item Walk down the steps, \cs[1:30], Time to keep movin', ya?
    \item Before goin' further, pick up the \pickup{Level 2 Key Sphere} and \pickup{Level 4 Key Sphere}, gonna need these, ya?
    \item \sd\ 'til Tidus asks ``why'', ya? \cs[6:20], Gotta figure out what's happenin', ya?
    \item \formation{\tidus}{\rikku}{\kimahri}, Set up the team, ya?
    \item Go bottom right to the next screen, run across the bridge, Let's go, ya?
\end{enumerate}
\winnp