\chapter{Airship, Ya?}

\begin{enumerate}
\item \sd\ during \cs+3 \skippablefmv. Gotta walk down the corridor to the next screen, then back again, ya?\sd. Talk to Brother, ya?\sd. Head towards the corridor, \sd. Walk towards the camera to the next screen, then go up, brudda.
\item If ya need more than, like, four Power Spheres, or any Speed Spheres, go buy Distillers from Rin, ya? Each one counts as two Spheres, ya know? Ya'll need twenty-eight Power Spheres and ten Speed Spheres for the rest of this pilgrimage, ya?
\item \save. Make sure that \rikku\ has \od. If she doesn't, ya can get into some random fights on Rin's first screen, ya know? Maybe she stole it? That Al Bhed...
\end{enumerate}
\begin{battle}[32000]{Evrae? Time for a Blitz!}
Turns in this fight can be, like, a bit random at times, ya know? Gotta treat each player on ya team independently, ya? Just do their action when their turn comes up! Just like in blitzball!
\begin{itemize}
\blitzballdetermination[true]{%
\tidusf Haste on \tidus
\tidusf Cheer on the team, Ya!
\tidusf If \tidus\ is still goin' next, right after his last move, change weapon to Sonic Steel, ya?
\rikkuf \od\ Mix a Luck Sphere with a Map, YA?
\tidusf Attack twice, brudda!
\tidusf Cheer
\tidusf Attack x3!
\item \kimahri\ or \rikku: Heal \tidus\ with an Elixir/X-Potion/Mega-Potion if he got hit in that first attack, ya? If not, Steal!
}{%
\tidusf Haste on \tidus
\tidusf Cheer x2
\tidusf Equip Baroque Sword, the one with Strength +5%, ya?
\tidusf Attack x6, ya!
\rikkuf \od\ Mix a Luck Sphere with a Map, ya?
\item \kimahri\ or \rikku: Gotta heal \tidus\ with an Elixir/X-Potion/Mega-Potion, use a Lunar Curtain on \tidus\ or Steal!
}
\end{itemize}
\end{battle}
\begin{enumerate}[resume]
\item \sd, \skippablefmv[3:00] - Press Start right after the FMV, Ya?
\end{enumerate}
\wincb