\chapter{Bevelle? Another Temple, Ya?}
\begin{enumerate}
\item Use a Mega-Potion, brudda! Gotta stay strong for Yuna's pilgrimage, ya know?
\ifthenelse{\equal{\blitzresult}{win}}{}{
\ifthenelse{\equal{\blitzresult}{both}}{
\item \textit{If ya \lostblitz: Time to get back in the game, brudda! Don't give up!}
}{}
\begin{equip}
\begin{itemize}
\tidusf Gotta Equip Sonic Steel, ya? Just like Tidus uses in blitzball, brudda!
\end{itemize}
\end{equip}
}
\item \textit{With Sleeping Powder, ya?}
\end{enumerate}
\begin{battle}{Guard Fights, Time for Sleeping Powder}
\begin{itemize}
\item \textit{Fights One and Three, That's Three Monks to deal with, ya?}
\begin{itemize}
\tidusf Attack 'em, Tidus! Show 'em what ya got!
\item Others: Defend or use Distillers, ya? Gotta be smart, like a good blitzball team!
\end{itemize}
\item \textit{Fights Two and Four, Two Monks and a YKT-63? What is this, machina?}:
\begin{itemize}
\tidusf Attack the YKT-63, that blasted machine!
\rikkuf Throw some Sleeping Powder, Rikku! Maybe those Al Bhed know how to use this stuff!
\kimahrif Gotta use a Smoke Bomb, or a Silence Grenade, or Sleeping Powder, Brudda Kimahri!
\blitzballdetermination[true]{}{%
\item \textit{If that YKT-63 is still alive} Use a Lightning Marble/Arctic Wind/Fish Scale, or Attack with \tidus, ya?
}
\end{itemize}
\item \textit{Fight Five, Two Monks and a YAT-99! More Machina!}:
\begin{itemize}
\item \textit{If ya got two Smoke Bombs/Sleeping Powders/Silence Grenades:}
\begin{itemize}
\tidusf Haste on Rikku, ya!
\rikkuf Sleeping Powder/Smoke Bomb/Silence Grenade, gotta stop 'em bruddas!
\rikkuf If the Guards are sleepin', use a Bomb Core on the YAT-99, ya!
\rikkuf Sleeping Powder/Smoke Bomb/Silence Grenade, Gotta keep them down!
\tidusf Attack, Ya!
\end{itemize}
\item \textit{If ya have two Bomb Cores:}
\begin{itemize}
\tidusf Attack the Monks, Ya!
\item Others: Use Bomb Core x2 on the YAT-99, blow that machine up!
\end{itemize}
\end{itemize}
\end{itemize}
\end{battle}
\begin{enumerate}[resume]
\item \textit{Without Sleeping Powder, No can do?}
\begin{itemize}
\item Keep \formation{\tidus}{\rikku}{\lulu} for the first four fights, Gotta keep \formation{\tidus}{\rikku}{\kimahri} for the last one, ya?
\end{itemize}
\end{enumerate}
\begin{battle}{Guard Fights, No Sleep!}
\begin{itemize}
\item \textit{Fights One and Three (Three Monks):}
\begin{itemize}
\tidusf Attack, ya! Show em' what you've got, brudda!
\item Others: Gotta Defend or use Distillers, ya? Focus up!
\end{itemize}
\item \textit{Fights Two and Four (Two Monks and a YKT-63): More Machina!}:
\begin{itemize}
\switch{\tidus}{\kimahri}
\kimahrif Silence Grenade/Smoke Bomb!
\rikkuf Silence Grenade/Smoke Bomb!
\switch{\kimahri}{\tidus}
\tidusf Attack that blasted YKT-63!
\blitzballdetermination[true]{}{%
\item \textit{If the YKT-63 is still alive} Use a Lightning Marble/Arctic Wind/Fish Scale, or Attack with \tidus!
}
\end{itemize}
\item \textit{Fight Five (Two Monks and a YAT-99):}:
\begin{itemize}
\item \textit{If ya have two Smoke Bombs/Silence Grenades:}
\begin{itemize}
\tidusf Haste Rikku, brudda!
\rikkuf Smoke Bomb/Silence Grenade x2!
\tidusf Attack, ya!
\end{itemize}
\item \textit{If ya have two Bomb Cores:}
\begin{itemize}
\tidusf Attack the Monks!
\item Others: Use Bomb Core x2 on the YAT-99!
\end{itemize}
\end{itemize}
\end{itemize}
\end{battle}
\begin{enumerate}[resume]
\item \sd, \skippablefmv[1:30], \sd\ on \yuna\ dialogue. \skippablefmv[30], \sd. Use the lift, \sd.
\end{enumerate}
\begin{trial}
\begin{itemize}
\item \textit{Upper section, YA?}:
\begin{itemize}
\item Push the pedestal in, ya?
\item Press X, Brudda.
\item Go left at the second junction, ya?
\item Take the sphere, push the pedestal back!
\item At the third junction, go back. Hold X, ya?
\item Go left at the second junction, brudda!
\item Place the sphere in the wall, push the pedestal back.
\item At the third junction, go back. Hold X, ya?
\item Go left at the first junction, hold X after the second junction, brudda.
\end{itemize}
\item \textit{Lower section, First visit ya?}:
\begin{itemize}
\item The platform's gonna stop at the first junction by itself, ya?
\item After it stops, press X the second time the arrow points left, ya?
\item Go right at the third junction, hold X after the second one, ya?
\item Grab the Glyph sphere from the wall, push the pedestal back, ya?
\item At the fourth junction, go right, hold X, brudda!
\item Put the Glyph sphere in the pedestal, ya?
\item Grab the Bevelle sphere from the pedestal!
\item Put the Bevelle sphere in the wall, ya?
\item Grab the Glyph sphere from the pedestal again!
\item Put the Glyph sphere in the next wall!
\item Take that Destruction sphere from the new wall, ya!
\item Put the Destruction sphere on the pedestal, Brudda!
\item Take the Bevelle sphere from the wall again!
\item Push the pedestal back and fall off the edge, brudda!
\end{itemize}
\item \textit{Lower section, Second visit, ya?}:
\begin{itemize}
\item Go straight, hold X before the platform stops, ya?
\item At the third junction, go right, hold X after the second junction, brudda!
\item Put the Bevelle sphere on the pedestal!
\item Take the Destruction sphere from the pedestal, ya?
\item Put the Destruction sphere in the wall, Brudda!
\item Push the pedestal back and fall off the edge.
\end{itemize}
\item \textit{Lower section, Third visit, ya?}:
\begin{itemize}
\item Go straight ahead, ya?
\item At the second junction, go right, hold X, Brudda!
\item Push that pedestal!
\item Go up the stairs, and open the chest, ya?
\end{itemize}
\end{itemize}
\end{trial}
\begin{enumerate}[resume]
\item \sd, name that Aeon \bahamut, don't save, \sd!
\end{enumerate}
\wincb\lossnp\bothnp\winnpsingle\lossnpsingle\bothnpsingle