\chapter{Via Purifico, Ya? Sounds Fishy!}

\begin{enumerate}
\item Run on up past the first telepad, Ya?
\item Head to the second telepad and travel north, like a blitzball headed for the goal, Ya?
\end{enumerate}
\begin{spheregrid}
\begin{itemize}
\auronf
\begin{itemize}
\item Move Right, Right, Right, like Auron heading into battle, ya?
\item Level Two Keysphere, gotta unlock Auron's potential, Brudda!
\item Move Right four times, or hold Right, to get there faster!
\item Level Two Keysphere, just like before!
\item Move Up, Up! (Or Up, Left if ya ain't on the right Node, ya?)
\item Magic plus three, ya!
\end{itemize}
\sggraphics{.7}{.4}{graphics/Auron_Via_Purifico}
\yunaf
\begin{itemize}
\begin{multicols}{2}
\item Move Up, Up, ya? Like Yuna climbin' the mountain, on her pilgrimage, brudda!
\item Level Four Keysphere, Gotta get there, brudda!
\item Move Right Three times, then Up, ya?
\item Strength plus two, Strength plus two, Strength plus two, that's how we get stronger, brudda!
\item Teleport Sphere to Auron's Magic Node, that's Up, ya?
\item Use the Magic Sphere, brudda!
\item Strength plus four, Magic plus three, Magic plus four, gotta make Yuna stronger, Ya!
\item Move Right, Right, Right, Up, like a blitzball team headin' down the field, ya?
\item Magic plus three, HP plus two hundred, Strength plus four, like a winning streak, brudda!
\item Move Right, brudda!
\item Defense plus three, Strength plus four!
\item Move Left, Down, ya?
\item Agility plus three, MP plus twenty, ya?
\item Move Left, Down, brudda!
\item HP plus two hundred, Strength plus two!
\item Move Down, Down, ya?
\item HP plus two hundred, Strength plus two, Magic plus three!
\item Level One Keysphere, Gotta unlock that grid, ya?
\item Move Southeast, Southeast, brudda!
\item Agility plus four, Strength plus two!
\item Move Left, Left, like a blitzball pass, ya?
\item Strength plus two, brudda!
\item Move Down, ya?
\item Strength plus two, MP plus twenty, Agility plus three!
\end{multicols}
\end{itemize}
\sggraphics{.7}{.4}{graphics/via_purifico_yuna_1}
\sggraphics{.7}{.4}{graphics/via_purifico_yuna_2}
\end{itemize}
\end{spheregrid}
\begin{enumerate}[resume]
\item Gotta get thirteen Power Spheres and seven Speed Spheres for the rest of the run, ya? That's how we win!
\item \save! Don't wanna lose progress, Ya?
\item Keep track of how many things ya kill here, ya?
\end{enumerate}
\begin{encounters}
\begin{itemize}
\item Maze Larva? Summon \ixion, then Attack, ya?
\end{itemize}
\end{encounters}
\begin{battle}{Isaaru! He thinks he's so great!}
\begin{itemize}
\item Grothia, 8000 HP, eh?
\begin{itemize}
\summon{\bahamut}, ya!
\bahamutf Attack, brudda! Show 'em what ya got!
\end{itemize}
\item Pterya, 12000 HP?
\begin{itemize}
\summon{\bahamut}, ya!
\bahamutf Attack, show em!
\end{itemize}
\item Spathi, 20000 HP?
\begin{itemize}
\summon{\ixion}, ya?
\ixionf Attack x4, gotta wear 'em down, brudda!
\end{itemize}
\end{itemize}
\end{battle}
\begin{enumerate}[resume]
\item Ya can use that underwater chest on the right at the start to buy a Speed Distiller, This is the last easy chance to grab Speed Spheres ya? Or grab a Power Distiller, ya know?
\item If ya need to, ya can attack a Phlegias or a Sahagin with \tidus\ for two Power Spheres. But only if it ain't an Ambush, ya?
\item Swim up, then up again when the camera changes, ya? Just like swimming to the blitzball!
\end{enumerate}
\begin{battle}{Evrae Altana? More like Evrae Al Bhed-ana! Probably built by those guys!}
\begin{itemize}
\item Anyone: Gotta use one Power/Speed Distiller if ya need it, ya?
\item Anyone: Use an Elixir/Phoenix Down twice on Evrae Altana! Gotta keep the team alive, ya?
\end{itemize}
\end{battle}
\begin{enumerate}[resume]
\item Swim to the exit, \sd.
\end{enumerate}
\bothnp\bothnpsingle