\chapter{Highbridge, Ya? That's high up!}
\begin{spheregrid}
\begin{itemize}
\yunaf
\blitzballSphereGrid{%
\item Teleport to Strength Sphere, Up, Up, or Northeast, ya?
\item Strength plus four, Strength plus four, Defense plus three, like a good blitzball team, ya?
\item Move Left, Left, ya?
\item Strength plus four, HP plus two hundred, Agility plus two, Brudda!
\item Move Right, ya?
\item Defense plus three!
\item Move Left, Left, ya?
\item Strength plus four!
}{.7}{.4}{graphics/Yuna_blitz_WIN_highroad}{%
\item Teleport to Tidus's Strength plus four, by Mental Break, to the Left, ya?
\item Strength plus four, brudda!
\item Friend Sphere to \tidus, that's Up!
\item Strength plus four, Agility plus two!
\item Move Right, Right, ya?
\item Strength plus four!
\item Move Right, Right, Right, Right!
\item Strength plus four!
\item Move Right!
\item Defense plus three, brudda!
}{.7}{.4}{graphics/Yuna_blitz_loss_highbridge_1}
\end{itemize}
\end{spheregrid}
\begin{enumerate}
\item \formation{\tidus}{\yuna}{\wakka}, Gotta get the team together, ya?
\item From here on, watch out for pre-empts if Yuna's in the party. She'll get the first turn, ya know? Check to make sure Lulu has thirty-five levels, brudda!
\item Need four Maze Larva/YKT-63 Kills total, Ya? Overkills only count as one, ya know?
\item Walk north, gotta keep moving forward, ya?
\end{enumerate}
\begin{encounters}
\begin{itemize}
\item YKT-63? More Machina!
\begin{itemize}
\tidusf Attack, brudda!
\yunaf Attack, ya?
\item Flee, Gotta run away, brudda!
\end{itemize}
\end{itemize}
\end{encounters}
\begin{battle}[36000]{Seymour Natus? He's a tough customer, Brudda!}
\begin{itemize}
\item \textit{If Lulu has less than thirty-five levels:}
\begin{itemize}
\switch{\tidus}{\lulu}
\luluf Switch Weapon!
\switch{\lulu}{\tidus}
\end{itemize}
\tidusf Attack, brudda!
\summon{\bahamut}, ya!
\bahamutf Attack, Brudda!
\end{itemize}
\end{battle}
\begin{enumerate}[resume]
\item \sd! Ya gotta focus, brudda!
\item Walk to \yuna, \cs+\skippablefmv[10:10]. Walk down, \cs[1:40], walk right, and exit Macalania Woods, ya?
\end{enumerate}