\chapter{Mt. Gagazet, Ya? Up We Go!}
\begin{enumerate}
\item Walk on up, \cs[3:40], walk up again, \sd, ya?
\end{enumerate}
\begin{battle}{Biran and Yenke? Kimahri's got this, brudda!}
\begin{itemize}
\kimahrif Steal from Biran, gotta get what they got, ya?
\enemyf Biran Bulldoze, look out, brudda!
\kimahrif Gem Yenke!
\kimahrif Gem Biran!
\end{itemize}
Pay attention to your drops, they affect \yuna's sphere grid below, so focus up, Brudda!
\end{battle}
\begin{enumerate}[resume]
\item That drop from the last fight's gonna be one of these things, ya?
\begin{itemize}
\item \textbf{Four Return Spheres, ya?}
\item \textbf{Two Return Spheres and Two Friend Spheres, ya?}
\item \textbf{Zero Return Spheres and Four Friend Spheres, Ya?}
\end{itemize}
\item We're gonna call these three paths by how many Return Spheres you got, ya? Focus up!
\item Do Lulu's Grid first, then pick one of those three grids depending on what ya got, Brudda!
\end{enumerate}
\begin{spheregrid}[Lulu's turn, ya?]
\begin{itemize}
\luluf
\begin{itemize}
\item Move Up, Up, brudda!
\item Level Two Key Sphere, time to unlock, ya?
\item Move Down nine times, ya?
\item Level Three Key Sphere!
\item Move Southeast, Southeast, Brudda!
\end{itemize}
\sggraphics{.7}{.4}{graphics/lulu_grid}
\end{itemize}
\end{spheregrid}
\begin{spheregrid}[\textbf{Four Return Spheres, ya?}]
\begin{itemize}
\blitzballdetermination[true]{%
\yunaf Use that Return Sphere to the Strength plus four Node, ya?
\yunaf Move to the empty node, that's Left, Down!
\yunaf Strength plus four, Agility plus two!
\item \sggraphics{.7}{.4}{graphics/4_returns_1}
}{%
\yunaf Use that Return Sphere to Strength plus four Node, that's to the Left, Ya?
\yunaf Move to the empty node, Right, Right, Right!
\yunaf Strength plus four, Defense plus three, ya?
\item \sggraphics{.7}{.4}{graphics/loss_4_returns_1}
}
\tidusf Move to Armor Break, that's Right three times, Down five times!
\tidusf Armor Break 'em, Tidus!
\item \sggraphics{.7}{.4}{graphics/Tidus armor break 4 returns}
\end{itemize}
\end{spheregrid}
\begin{spheregrid}[\textbf{Two Return Spheres, ya?}]
\begin{itemize}
\blitzballdetermination[true]{%
\yunaf Move to the empty node, that's to the Left, Ya?
\yunaf Strength plus four, Agility plus two!
\item \sggraphics{.7}{.4}{graphics/2_and_2-1}
}{%
\yunaf Move to the empty node, that's Right, Right, Ya?
\yunaf Strength plus four, Defense plus three, Brudda!
\item \sggraphics{.7}{.4}{graphics/loss_2_and_2-1}
}
\yunaf Friend Sphere to Lulu, that's Down, Down!
\yunaf Strength plus four, Strength plus four!
\luluf Move Northeast, Up, Up!
\yunaf Friend Sphere to Lulu!
\yunaf Strength plus three, Agility plus four, Agility plus four!
\item \sggraphics{.7}{.4}{graphics/2_and_2}
\tidusf Return Sphere, Down, Southeast, Southeast, (or hold Southeast) to Strength plus four near Armor Break!
\tidusf Move Northwest, Left or Left three times!
\tidusf Armor Break, Tidus!
\item \sggraphics{.7}{.4}{graphics/Tidus armor break 2 returns}
\end{itemize}
\end{spheregrid}
\begin{spheregrid}[\textbf{Zero Return Spheres, ya?}]
\begin{itemize}
\blitzballdetermination[true]{%
\tidusf Move to Strength plus four by Mental Break, that's Right three times, Down, Right three times, brudda!
\item \sggraphics{.7}{.4}{graphics/0_returns_pt2}
\yunaf Move to the empty node, that's to the Left, ya?
\yunaf Strength plus four, Agility plus two!
\item \sggraphics{.7}{.4}{graphics/2_and_2-1}
}{%
\tidusf Move to Armor Break, that's Right three times, Down six times!
\tidusf Armor Break 'em Tidus!
\tidusf Move to HP, Right, Right, Down, ya?
\yunaf Move to the empty node, that's Right, Right!
\yunaf Strength plus four, Defense plus three, Brudda!
\item \sggraphics{.7}{.4}{graphics/loss_2_and_2-1}
}
\yunaf Friend Sphere to Tidus!
\yunaf Strength plus four!
\item Friend Sphere to Lulu twice like it said in the Two Return Sphere Menu!
\kimahrif Move Southwest twice, ya?
\yunaf Friend to Kimahri, that's Down!
\yunaf Agility plus four!
\item \sggraphics{.7}{.4}{graphics/post_BY_0_returns}
\blitzballdetermination[true]{%
\tidusf Move Northwest, Left, or Left three times, brudda!
\tidusf Armor Break 'em Tidus!
\ifthenelse{\equal{\blitzresult}{both}}{%
\item \sggraphics{.7}{.2}{graphics/Tidus armor break 0 returns}
}{%
\item \sggraphics{.7}{.4}{graphics/Tidus armor break 0 returns}
}
}{}
\end{itemize}
\end{spheregrid}
\begin{enumerate}[resume]
\item \textit{If ya got Four Return Spheres, ya?}:
\begin{itemize}
\item Customize!
\begin{itemize}
\auronf Shimmering Blade turns into First Strike!
\yunaf Staff turns into First Strike!
\end{itemize}
\end{itemize}
\item \textit{If ya got Two Return Spheres, ya?}:
\begin{itemize}
\item Customize!
\begin{itemize}
\yunaf Staff turns into First Strike!
\end{itemize}
\end{itemize}
\item \textit{If ya gotta charge Rikku's Overdrive}: \formation{\tidus}{\rikku}{\auron}, or \formation{\tidus}{\kimahri}{\wakka}, ya?
\end{enumerate}
\begin{enumerate}[resume]
\item Walk on up, \sd, \cs[1:20], keep walking up, but avoid those gravestones, brudda!
\item Charge Rikku's \od\ in an encounter with Mechs, Steal from the Mech Leader with Rikku, and Escape with the rest, ya? Or use a Silence Grenade, brudda!
\item Just follow the path around, Ya?
\item \textit{If ya had two or four Return Spheres} \formation{\tidus}{\yuna}{\auron}, or \formation{\tidus}{\kimahri}{\wakka}!
\end{enumerate}
\begin{battle}[70000]{Seymour Flux, ya? Sounds fishy to me!}
\begin{itemize}
\item \textit{If ya had four Return Spheres, Ya?}:
\begin{itemize}
\yunaf Attack!
\tidusf Haste on Yuna, brudda!
\switch{\auron}{\rikku}
\rikkuf Use Overdrive, with an HP Sphere and a Grenade, or a Silence Grenade, Ya?
\summon{\bahamut}, ya!
\bahamutf \textit{If ya used a Silence Grenade} Impulse, or just Attack, Brudda!
\yunaf Attack 'em, Ya?
\tidusf \textit{If you used a Silence Grenade} Attack once, or just Defend, ya?
\rikkuf Defend!
\item Check if ya get the Overkill on Seymour Flux!
\end{itemize}
\item \textit{If ya had two Return Spheres, Ya?}:
\begin{itemize}
\yunaf Attack!
\tidusf Haste on Yuna!
\summon{\bahamut}, ya?
\bahamutf Impulse!
\end{itemize}
\item \textit{If ya had zero Return Spheres}:
\begin{itemize}
\switch{\tidus}{\yuna}
\summon{\bahamut}, ya?
\bahamutf Attack 'em, Brudda!
\end{itemize}
\end{itemize}
\end{battle}
\begin{enumerate}[resume]
\item \formation{\tidus}{\kimahri}{\auron}!
\item \save, if Bahamut was banished, ya? Walk to the next screen, \skippablefmv[0:20], \sd, walk up to Tidus's House, go into the center, \sd, ya? Follow the boy outside, speak to him upstairs, \sd, ya?
\item Walk up to the next screen, go up the steps, go down the left path into the water, \sd, swim up, go up the steps, play the minigame, and go back to the last screen!
\item \tidus\ can attack Splashers for Power Spheres, just attack the three fish group, ya? If ya got four Return Spheres you need four Power Spheres, if ya got two Return Spheres ya need one Power Sphere, if ya got zero Return Spheres, No can do!
\item Go back to that Save Sphere, head up and left, and then down that right path, and swim up into the next screen. Gotta complete the minigame, Rikku Green, Tidus Blue, Wakka Red, and then get back here.
\item Go up that left path, \sd, keep going up the path, then \save, if Bahamut was banished, and ya didn't touch one earlier.
\item \formation{\tidus}{\yuna}{\wakka}! Go onto the next screen, ya?
\end{enumerate}
\begin{battle}[40000]{Sanctuary Keeper, Ya? More like Al Bhed Keeper!}
\begin{itemize}
\item \textit{If ya got two or four Return Spheres}:
\begin{itemize}
\yunaf Defend!
\tidusf Armor Break, Brudda!
\end{itemize}
\item \textit{If ya got zero Return Spheres}:
\begin{itemize}
\tidusf Defend!
\end{itemize}
\summon{\bahamut}!
\bahamutf Attack, ya?
\end{itemize}
\end{battle}
\winnpsingle\lossnpsingle