\chapter{Airship, ya? Almost there, Brudda!}
\begin{enumerate}
\item \sd, gotta focus up, ya? Walk out the cockpit past Rin, along those corridors to Yuna and Kimahri, Ya? \sd. Walk back to the cockpit, \sd, Talk to Cid, Gotta travel to the Highbridge, Ya!
\item Walk up to the Bevelle entrance, ya know? \sd. In the Fayth room, pick that first choice, ya, I Think So'', then pick the second one, GottaDefeat Yu Yevon''!
\item Walk up to Cid, gotta travel to Sin! \sd, \skippablefmv, \sd. Go through the corridors to the outside of the airship, brudda! \sd, three \skippablefmv[2:10], \sd.
\end{enumerate}
\begin{battle}[65000]{Sin Left Fin, Time to take it down!}
\begin{itemize}
\summon{\bahamut}, ya?
\bahamutf Impulse x2! Show it what you got, brudda!
\end{itemize}
\end{battle}
\begin{enumerate}[resume]
\item \sd, Ya know, gotta focus! \cs+\skippablefmv.
\end{enumerate}
\begin{battle}[65000]{Sin Right Fin, Time to bring it down too!}
\begin{itemize}
\summon{\bahamut}, ya?
\bahamutf Impulse x2!
\end{itemize}
\end{battle}
\begin{enumerate}[resume]
\item \sd, ya gotta focus! \cs+\skippablefmv!
\end{enumerate}
\begin{battle}[56000]{Sin Genais and Core, We gotta finish this now!}
\begin{itemize}
\summon{\bahamut}, ya?
\bahamutf Impulse the Core! Gotta get to the heart of the matter, Ya?
\end{itemize}
\end{battle}
\begin{enumerate}[resume]
\item \sd, and \skippablefmv, Ya?
\item Walk along the corridors to outside the ship, speak to Yuna, ya? \cs[1:40], \sd, that Al Bhed Rikku dialogue, \skippablefmv, Go through those corridors, go outside again, \skippablefmv, \sd, ya know?
\end{enumerate}
\begin{battle}[140000]{Overdrive Sin, ya? Time to win!}
\begin{itemize}
\summon{\bahamut}, ya?
\bahamutf Impulse, Ya?
\bahamutf Attack x2! Show em how it's done, brudda!
\end{itemize}
\end{battle}
\begin{enumerate}[resume]
\item \skippablefmv[1:20], \sd.
\end{enumerate}